### 2016-05-13 Documents/bootcamp_topic_pyfun2.tex
Added documents

\documentclass[11pt]{article}

\input{../LaTeX/preamble.tex}

% document starts here
\begin{document}
\parskip=\bigskipamount
\parindent=0.0in
\thispagestyle{empty}
\input{../LaTeX/header.tex}

\bigskip\bigskip
\centerline{\Large \bf Topic Outline:  Python Fundamentals 2}
\centerline{Revised: \today}

\section*{Materials}

\begin{itemize}
\item  Today's handouts:  this outline, book chapter, code practice, stickers
\item  All posted on {\it Topic outlines \& links\/} page of website (except the stickers).
\end{itemize}

\section*{Preliminaries}

\begin{itemize}

\item Tools and buzzwords
\begin{itemize}
\item Boolean variables, comparisons, conditionals ({\tt if}, {\tt else}), slicing,
loops ({\tt for}), function definitions.
\end{itemize}

\item Rules to live by:  don't panic, ask for help

\item What is this?
\begin{itemize}
\item \verb|'abcd' |
\item \verb|['Chase', 'Dave', 'Sarah', 'Spencer'] |
\item \verb|('Chase', 'Dave', 'Sarah', 'Spencer') |
\item \verb|'98.76'|
\item \verb|float('98.76')|
\item \verb|int(float('98.76'))|
\item \verb|len('98.76')|
\item \verb|list('abcd')|
\item Tab completion
\item {\tt object.method?}
\item Object inspector
\end{itemize}

\item {\bf Exercise}
\begin{itemize}
\item Put red sticker on your laptop
\item Start Spyder
\item Open new file  \verb|bootcamp_class_pyfun2.py|
in your \verb|Data_Bootcamp| directory
\item Replace red sticker with green when you're set
\end{itemize}

\end{itemize}

\section*{Python fundamentals 2}

We'll follow the book chapter.
\begin{itemize}
\item Dictionaries
\item Logical expressions (comparisons)
\item Conditionals
\item Slicing strings and lists
\item Loops over lists and strings ({\tt for}, {\tt else})
\item Loops over counters ({\tt range()})
\item Defining functions
\item Style
\item Review
\begin{itemize}
\item Put red sticker on, replace with green when done
\end{itemize}
\end{itemize}

\section*{Examples}

If time permits, we'll go through some examples of economic and financial data
and its properties.  It's an IPython notebook that you can view on the GitHub repo:
the \verb|Code/IPython| directory,
file \verb|bootcamp_examples.ipynb|.

\section*{After class}

\begin{itemize}
\item Required
\begin{itemize}
%\item Review this chapter
\item Code Practice \#2 (should take about an hour)
\end{itemize}
\item Recommended
\begin{itemize}
\item {\bf Write}:  After class, write down everything you remember without using your notes
\item {\bf Review:} Reread the chapter and fill in anything you missed.
\item Ask for help if you get stuck.
\end{itemize}
\end{itemize}

\input{../LaTeX/footer.tex}

\end{document}

### 2016-08-17 Documents/bootcamp_syllabus.tex
Started updating syllabus for this year:

\documentclass[11pt]{article}

\input{../LaTeX/preamble.tex}

% document starts here
\begin{document}
\parskip=\bigskipamount
\parindent=0.0in
\thispagestyle{empty}
\input{../LaTeX/header.tex}

\bigskip\bigskip
\centerline{\Large \bf Data Bootcamp:  Syllabus}
\centerline{Revised: \today}

\section*{Overview}

Data Bootcamp is about nuts and bolts data analysis. You will learn about economic, financial, and business
data, and enough about computer programming to work with it effectively.
Applications include some or all of: leading economic indicators; emerging market country indicators;
bond and equity returns; stock options; education and income; income by zip code; long tail sales data; innovation diffusion curves; and many others.
We will use Python, a popular high-level computer language that's widely used in finance, consulting,
technology, and other parts of the business world.
``High-level'' means it's less painful than most (the hard work is done by the language),
but it's a serious language with extensive capabilities.
``Data analysis'' means primarily graphical descriptions that summarize data
in ways that are helpful and informative.
``Bootcamp'' is a reminder that expertise takes work. Don't worry, it's worth it.
{\bf You will be more valuable to current and future employers.\/}
And you will be able to do more things more efficiently than
friends who rely on Excel.

If you're not convinced --- or even if you are ---
we have a more elaborate sales pitch on the
\href{http://databootcamp.nyuecon.com/}{course website}.

There are two sections of this course,
one for undergrads (ECON-UB.0232) and one for MBA students (ECON-GB.2313).
The content is the same, but the schedules are different.

\section*{Requirements}

There are no prerequisites.
{\bf We welcome students with no prior programming experience\/}
and have designed the course with them in mind.
What you need is the {\bf courage\/} to take on a challenge
and the {\bf patience\/} to fix computer programs that don't work.
That's a regular occurrence, even for experts.

Our one requirement is that {\bf you must bring a laptop computer to class\/}.
It should be your own computer, or at least one you can install new programs on.
We will use it constantly in class, writing and correcting short programs.

\section*{Getting help}

This course has a strong {\bf support system\/} to help you when you run into problems ---
and anyone who codes runs into problems.
Each section has two teachers and a teaching assistant, all of them happy to answer your questions.
You  can also post questions on our discussion group (see below).

The bottom line:  {\bf If you're stuck, ask for help\/}.
Really.  Don't be a hero, ask for help.

\section*{Course website and discussion groups}

Eveything you need, including this document, is posted on
the {\bf course website\/}:
%
\vspace{-0.15in}
\begin{center}
\url{http://databootcamp.nyuecon.com/}
\end{center}
\vspace{-0.15in}
%
The {\bf book\/} has its own site,
% TODO: We need to change this link once gitbook is re-enabled
\vspace{-0.15in}
\begin{center}
\url{https://www.gitbook.com/book/davebackus/test/details}
\end{center}
\vspace{-0.15in}
%
There's a link to it on the course site.
We will not use NYU Classes.

We have set up {\bf announcement and discussion groups\/} (Google groups)
to make announcements and post questions. We will use this to post all assignments and
answer keys.
If you have coding or other questions, we encourage you to post them there.
If you know the answer to someone else's question, we {\bf strongly } encourage you to post that, too.
The links are
% TODO: we need to update these links once we decide where our forum will go
\vspace{-0.1in}
\begin{center}
UG:   \url{https://groups.google.com/forum/#!forum/nyu_data_bootcamp_ug}  \\
MBA:  \url{https://groups.google.com/forum/#!forum/nyu_data_bootcamp_mba}
\end{center}
\vspace{-0.1in}
%
You can access the same links from the course website.  Follow the instructions to join under whatever email address you plan to use.

\section*{Deliverables and grades}

The course divides naturally into two parts.
The first part is an introduction to those aspects of the Python programming language
useful for data analysis.
We cover this material with as many applications to real data as we can think of.
It ends with an exam.
The second part covers advanced topics and ends with a project of your own.
The goal is for you to have a piece of work you can show potential employers to
illustrate your quantitative skill set.
Both parts include a number of graded deliverables.
The idea is to {\bf do some work all the time rather than lots of work once in a while.}
We don't believe the latter will work.

Graded work includes:
%
\begin{itemize}

\item {\bf Code Practice.\/}
There are three such assignments in the first month.
We encourage you do to all of them --- they're good practice ---
but your grade will be based on the best two.
We will also distribute Optional Code Practice ``assignments,''
but they will not be collected or graded.
They are, however, a good way to develop your coding skills.

{\it These assignments have questions that range from easy to moderately difficult,
the latter marked {\it challenging\/}.
They're all good practice, but if you're new to programming you
might want to skip the challenging ones.
If you get 70-80 percent of them, you're on the right track. \/}

\item {\bf Examination.\/}
The exam will cover material from the first half of the course.
It takes 75 minutes and will be held in class.
It will involve coding.
{\bf Bring your computer.\/}
We suggest you also {\bf bring one page of notes\/}.
If the internet is working you will be able to look things up on there.
If not, your notes will save you.
It's also a good study tool:  When you decide what to include,
you'll be organizing your thoughts about what you've learned.

\item {\bf Project.\/}
We work our way up to the project one step at a time, starting with idea generation and ending
with a {\bf professional piece of data collection and analysis\/}
that you can share with potential employers.
The structure of the project is laid out in a separate document.

\end{itemize}

{\bf Due dates} are posted on the course website.
Assignments, whether code practice or components of the project,
are due at the start of class on the specified dates.
{\bf Dates are not negotiable.
Anything handed in late will get a grade of zero.\/}

{\bf All your work should be clean and professional.}  Your grade depends on it.

{\bf Final grades\/} will be computed from
\begin{center}
\begin{tabular}{ll}
Code Practice (best two of three) & 20\% \\
Exam        & 30\% \\
Project     & 50\% \\
\end{tabular}
\end{center}
Final grades are not subject to any fixed distribution or curve.
The number of A grades, for example,
will depend only on your performance in the course.
If you make a good-faith effort,
we expect it to be hard to get less than a B.
We are the sole judges of what constitutes good-faith effort.

\section*{Recommended work habits}

Python is not something you can learn from reading a book and attending lectures.
You need to {\bf write programs\/} ---
the more the better --- to understand how they work.
Think about how you'd learn to play basketball or soccer;
reading and listening to lectures aren't enough, you need to do it.
We'll do a lot of programming in class, but it's {essential\/} that you
follow up outside of class.
Here's how.

{\bf Write \& Review.\/}
After each topic, we recommend you:
% write everything you remember without looking
%at your notes or the book.  Note any gaps in your knowledge.
%Then read the book, work through the exercises, and fill in the gaps.
%Ask
%
%\begin{comment}
\begin{itemize}
\item {\it Write:\/}  Shortly after class, write down everything you remember
without looking at your notes or the book.
Note things you don't understand --- gaps, we call them.
\item {\it Review:\/} Read the relevant section of the book.  Fill in the gaps.
Ask for help with anything you still don't understand.
%\item {\bf Review:\/} Later on, go through what you wrote down earlier and  fill in the gaps
%by using the book.
\end{itemize}
%\end{comment}
%

{\bf Practice.\/}
For the first half of the term, each topic has an assignment that covers the same material.
We suggest you do them, even the ones that aren't graded.

We also recommend you {\bf practice coding\/} whenever you have the chance.
Start small. Write short programs to do anything that crosses your mind.
Use Python to do things you would ordinarily do in Excel.
Try doing assignments from other courses in Python.
At first this will be more work than doing it by hand or in Excel,
but once you have some experience it will typically be easier in Python.
Even if that's not the case, the practice will expand your skill set.

\section*{Pacing}

The course is designed to be cover material at whatever pace the class is capable of.
The topics should take roughly one week each, but we can scale that up or down as needed.
If you're an expert, don't worry, we'll cover a lot of material either way.

\section*{Other questions}

% TODO: we need to fix the email address below once we finish setting up the domain
You can find answers to common questions on the course website.
You can also post questions on the discussion group;
see the link above and on the course website.
For others, email us (\href{mailto:nyu.databootcamp@gmail.com}{nyu.databootcamp@gmail.com}),
the co-teacher, or the teaching fellow; their contact information is on the course website.

\section*{Viewing and printing pdf files}

This document and most others in the course are pdf's that we hand out in class and post on GitHub.
If you view them online, the links won't work; that's an unfortunate feature of GitHub's pdf viewer.
You should instead download them to your own computer and open them there.
To download them,
click on the Raw button above the document.
To view them, use Adobe Acrobat Reader or the equivalent (FoxIt, Sumatra, etc).
The links should then work.

For Mac OS users, Preview has this problem and others; for example,
links don't work and some fonts don't display or print.
The solution is to install Adobe Acrobat Reader or the equivalent
and set it up as your default for pdf files.

\section*{Policies}

Ethics, disabilities, and many other things are governed by NYU
and Stern policies.
If you have questions about them, please ask.

On graded work:
You may discuss assignments with anyone (in fact, we encourage it),
but anything you submit, including your code, should be your own.
Exams should be entirely your own work.

On disabilities:
If you have a qualified disability that requires academic accommodation,
please contact the Moses Center for Students with Disabilities
(\href{http://www.nyu.edu/life/safety-health-wellness/students-with-disabilities.html}{CSD},
212-998-4980) and ask them to
send me a letter verifying your registration and outlining the accommodation they recommend.
If you need to take an exam at the CSD,
you must submit a completed Exam Accommodations Form to them
at least one week prior to the scheduled exam time to be assured accommodation.

\input{../LaTeX/footer.tex}

\end{document}

OLD STUFF

\begin{itemize}
\item Data. We live in a world that's ...
\item Programming. To make sense of the data, you need to be able to code:
to write computer programs to put the data in a form that ...
Be forwarned:  you are expected to write programs in this course.
This can be incredibly frustrating and requires enormous patience.
If that's not your thing, you should not take this course.
\item Graphics.
\end{itemize}

### 2016-09-06 Documents/bootcamp_practice_3.tex
rebuild all text documents to show updated header and date

\documentclass[11pt]{exam}

\input{../../LaTeX/preamble.tex}

%\printanswers

% document starts here
\begin{document}
\parskip=\bigskipamount
\parindent=0.0in
\thispagestyle{empty}
\input{../../LaTeX/header.tex}

\bigskip\bigskip
\centerline{\Large \bf Data Bootcamp:  Code Practice \#3}
\centerline{Revised: \today}

{\it Answer each of the questions below.
We recommend code with comments.
Please submit in hardcopy.}

The data input parts of each question are included in this template:

\vspace{-0.06in}
{\small
\url{https://raw.githubusercontent.com/NYUDataBootcamp/Materials/master/Code/Python/bootcamp_practice_3_template.py}
}
\vspace{-0.06in}

Or just navigate from the GitHub page:  \\
Code $\Rightarrow$ Python $\Rightarrow$ \verb|bootcamp_practice_3_template.py| $\Rightarrow$ click on Raw button

% \begin{solution}
% Short answers follows.
% The code is attached; download this pdf file,
% open it with the Adobe Reader or the equivalent,
% and click on the pushpin:
% \attachfile{../Code/Answers/bootcamp_practice_3_answerkey.py}
% \end{solution}

\begin{questions}
\item Enter and run this code in Spyder to produce the dataframe \texttt{weo}:
%\vspace{-0.15in}
\begin{verbatim}
import pandas as pd
data = {'BRA': [13.37, 13.30, 14.34, 15.07, 15.46, 15.98, 16.10],
        'JPN': [33.43, 31.83, 33.71, 34.29, 35.60, 36.79, 37.39],
        'USA': [48.30, 46.91, 48.31, 49.72, 51.41, 52.94, 54.60],
        'Year': [2008, 2009, 2010, 2011, 2012, 2013, 2014]}
weo  = pd.DataFrame(data)
\end{verbatim}
%\vspace{-0.15in}
The numbers are GDP per person in thousands of US dollars, 2008 to 2014,
variable PPPPC in the IMF's {\it World Economic Outlook\/} database.

\begin{parts}
\item Explain the \texttt{import} statement.
\item What type of object is {\tt data}?
\item Why does the last line have {\tt pd} prior to the {\tt DataFrame} function?
\item What type of object is {\tt weo}?
\item How many rows does it have?  Columns?
\item What {\tt dtypes} are the variables/columns?  What does this mean?
\item {\it Challenging.\/}
What are each of these expressions?  What type?
\begin{verbatim}
weo['Year']
weo[['Year']]
weo[[3]]
\end{verbatim}
\item {\it Challenging.\/}
Find and apply a method to convert {\tt weo['Year']} to type {\tt float}.
{\it Hint:\/} The method begins with the letter {\tt a}.
\item Describe the result of the statement \texttt{t = weo.tail(3)}.
What kind of object is \texttt{t}?  What does it look like?
\item How would you create a new dataframe that consists of the first 4 rows of \texttt{weo}?
\item What type of object is \texttt{weo['BRA']}?
\item Create a new variable equal to the ratio of Brazil's GDP per capita to Japan's.
\item {\it Challenging.\/}
Use the {\tt drop()} method to eliminate this (new) variable from the dataframe.
\item What are {\tt weo}'s row and column labels?
\item Set the index equal to the {\tt Year} variable.
\item Change the names of the other variables to Brazil, Japan, and United States.
\item Export the dataframe to an Excel spreadsheet.
\item What method would you use to compute the mean for each country?
What are the means?
\item {\it Challenging.\/}
How would you compute means across countries for each year?
\item Plot the data by applying a {\tt plot} method to {\tt weo}.
\item {\it Challenging.\/} Change the colors of the lines to green (Brazil), red (Japan),
and blue (US).
\item {\it Challenging.\/}
Do the same plot with a log scale.
{\it Hint:\/} Read the documentation for the plot method.
\item Plot Brazil on its own.
\end{parts}

\begin{solution}
\begin{parts}
\item The {\tt import} statement adds the {\tt pandas} data management package.
\item Dictionary --- note the curly braces.
\item The {\tt pd.} identifies {\tt DataFrame} as a pandas function.
\item Dataframe.
\item {\tt weo.shape} tells us that {\tt weo} has 7 rows and 4 columns.
\item {\tt weo.dtypes} generates the output
\begin{verbatim}
BRA     float64
JPN     float64
USA     float64
Year      int64
\end{verbatim}
So the first three variables are floats, the last one is an integer.
\item Apply the type function.  The first one is a series, the last two are
dataframes.
The difference here is the input.  If the input is a string, it returns a variable.
If the input is a list, it returns a dataframe.  The content is similar, but they're
(slightly) different objects.
This isn't particularly important, other than to remind ourselves that
the details matter here.

\item We use:  {\tt weo['Year'] = weo['Year'].astype(float)}.
The right side changes the type to float, then we assign it back to {\tt weo['Year']}.

\item {\tt t = weo.tail(3)}
is a dataframe consisting of the last three rows of {\tt weo}.

\item {\tt  weo.head(4)}.

\item A series, a single variable (column).

\item Use the statement:  {\tt weo['ratio'] = weo['BRA']/weo['JPN']}.

\item Use: {\tt weo = weo.drop(['ratio'], axis=1)}.

\item We get (and print) the row and column labels with
\begin{verbatim}
print('Row labels (index):', weo.index)
print('Column labels:', weo.columns)
\end{verbatim}

\item \verb|weo = weo.set_index(['Year'])|.

\item \verb| weo = weo.rename(columns={'BRA': 'Brazil', 'JPN': 'Japan', | \\
      \verb|                           'USA': 'United States'})|

\item \verb|weo.to_excel('weo.xls')|

\item {\tt print('Country means:', weo.mean(), sep='')}

\item {\tt print('Year means:', weo.mean(axis=1), sep='')}

\item {\tt weo.plot()}
(The year labels are messed up here, we'll have to fix that/)

\item {\tt weo.plot(color=['green', 'red', 'blue'])}

\item There's an ambiguity here over whether to use logs on the x axis, the y axis, or both.  This does the y axis:  \\ {\tt weo.plot(color=['green', 'red', 'blue'], logy=True)}

\item {\tt weo['Brazil'].plot()}

\end{parts}
\end{solution}

% ----------------------------------------------------------------------------
\item Use \verb|read_csv()| to read the responses of our class entry poll from

\vspace{0.1in}
\centerline{\url{http://pages.stern.nyu.edu/~dbackus/Data/Data-Bootcamp-entry-poll_s16.csv}}
\vspace{0.1in}

\begin{parts}
\item Read the file and assign it to the variable {\tt ep}.
\item Describe its contents.  What are the variables?  The responses?
\item What data types are the variables?
\item Change the variable names to something shorter.
\item {\it Challenging.\/}
Describe what this code does:
\begin{verbatim}
ep[list(ep)[1]].value_counts()
\end{verbatim}
{\it Suggestion:\/} Break it into two or more statements and explain them one at a time.
\end{parts}

\begin{solution}
\begin{parts}
\item \verb|ep = pd.read_csv(url)|
\item You can see them at the source.  The file is a ``dump''
of questions (the variable names) and answers (the data).
It's somewhat verbose, which makes it hard to print out and look at.

\item The dtypes are all objects:  strings.

\item The names are so long it's easier to replace all of them with
\begin{verbatim}
ep.columns = ['time', 'program', 'career', 'code_exp', 'stats_exp',
              'media', 'other', 'major', 'data', 'why', 'topics']
\end{verbatim}

\item This is practice with breaking complicated code into manageable pieces:
\begin{itemize}
\item {\tt list(ep)} is a list of variable names, each of them strings
\item {\tt list(ep)[1]} is the second variable name, \\
{\tt 'What program are you enrolled in?'},\\
or its replacement {\tt program}.
\item {\tt ep[list(ep)[1]]} is the second variable --- a series.
\item \verb|ep[list(ep)[1]].value_counts()|  applies the
\verb|value_counts()| method, which lists the number of each response to the question.  Here we get
\begin{verbatim}
MBA                             46
Undergraduate business          36
Other undergraduate             13
\end{verbatim}
and a collection of other responses with one or two each.

\end{itemize}

%\begin{verbatim}
%\end{verbatim}

\end{parts}
\end{solution}

% ----------------------------------------------------------------------------
\item  Consider the 538 college majors data at {\tt url}:
\begin{verbatim}
url1 = 'https://raw.githubusercontent.com/fivethirtyeight/data/master/'
url2 = 'college-majors/recent-grads.csv'
url = url1 + url2
\end{verbatim}
The variables are described at

\vspace{0.1in}
\centerline{\url{https://github.com/fivethirtyeight/data/tree/master/college-majors}}
\vspace{0.1in}

\begin{parts}

\item Create a dataframe {\tt df538} from the csv file at {\tt url} using
\verb|read_csv()|.
What are its dimensions?

\item What argument/parameter would you use to read only
the first ten lines of the file?

\item Extract the variables numbered \texttt{[2, 4, 15, 16, 17]}.
What are the names of these variables?
What do they represent?

\item Set the index equal to {\tt Major}.

\item Use the \verb|sort_values()| method to sort the data by {\tt Total}.

\item What code would you use to extract the ten majors with the greatest number of people?

\item {\it Challenging.\/}
Construct horizontal bar charts of the top ten majors sorted, first, by median salary
and, second, by the salary of the 25th percentile.
In each case plot just the variable you sorted on.
\end{parts}

\begin{solution}
\begin{parts}
\item Use the code:  \verb|df538 = pd.read_csv(url)|

\item {\tt nrows=10}.

\item The variables are total (the total number for this major),
median (median salary), P25th (25th percentile salary),
and P75th (75th percentile salary).
The last three describe the overall distribution of salaries:
the 25th, 50th, and 75th percentiles.

\item \verb|df = df.set_index(['Major'])|

\item \verb|h = df.head(10)|

\item \verb|h['Median'].sort_values().plot(kind='barh')|
\item \verb|h['P25th'].sort_values().plot(kind='barh')|

\end{parts}
\end{solution}

\item Approximately how long did this assignment take you?

\end{questions}

\input{../LaTeX/footer.tex}

\end{document}

### 2016-09-06 Documents/bootcamp_project.tex
rebuild all text documents to show updated header and date

\documentclass[11pt]{article}

\input{../LaTeX/preamble.tex}

% document starts here
\begin{document}
\parskip=\bigskipamount
\parindent=0.0in
\thispagestyle{empty}
\input{../LaTeX/header.tex}

\bigskip\bigskip
\centerline{\Large \bf Data Bootcamp:  Project Guide}
\centerline{Revised: \today}

\section*{Overview}

One of our goals is for you to produce a piece of work you can use
to demonstrate your data and programming skills to potential employers.
That work will come in the form of an IPython/Jupyter notebook,
a format that combines code, text, and graphics in one user-friendly document.
We will add them to our GitHub repository so that
you can use a link to show others what you've done.
You will also be able to see what your classmates have done.

The relatively loose structure in self-directed projects like this
makes them more challenging than most things you do in school.
We think that also makes them more interesting.
They give you a chance to
indulge your curiosity and show off your creativity.

We have divided the project into components to keep you on track.
The intent is to make the project easier by breaking it down into a number
of small, manageable sub-projects.
The early steps are graded only on whether you do them:
you get 5 points if you do them, none if you don't.
We start with individual work.  Partway along, we encourage you to form groups
of two or three, but if you'd prefer to do this on your own,
that's ok, too.

\section*{Project outline}

The components of the project are
%
\begin{center}
\begin{tabular}{lllr}
\toprule
Assignment                  & Format  & Individual/Group &  Points \\
\midrule
Three Project Ideas         & Paper (hand-written)  & Individual  & 0  \\
Three Revised Project Ideas & Paper (professional)  & Individual  & 5  \\
Project Proposal            & Paper (professional)  & Group       & 5  \\
Data Report                 & Paper (professional)  & Group       & 5  \\
Final Project               & IPython/Jupyter notebook      & Group       & 85 \\
\bottomrule
\end{tabular}
\end{center}

The due dates are posted on the {course website}.
%{\bf Dates are firm and not open for negotiation.}

The components consist of:
\begin{itemize}

\item {\bf Three project ideas.}
Write down three project ideas in class.
One or two sentences each is enough.
Use your imagination.  Be creative.  Speak to others.
Write down things that interest you.
This will not be graded, but it will give you something to work with later on.

Over the coming weeks, we recommend you keep your ears open for possible
{\bf project ideas} --- and {\bf data sources\/}.

\item {\bf Three revised project ideas.}
After giving this more thought, write down three project ideas in (a little) more detail.
{\bf Include likely data sources.}
%Ask questions; we have a lot of experience with this, especially data.
All together this should be roughly one paragraph per idea and one page overall.
Like all work in this course, it should be clean and professional.
%We will keep the copy you hand in to use in class, so keep a separate copy for yourself.

{\bf We will not give you written feedback} on your ideas,
but {\bf we would be happy to talk in person}, either before class or another time.
Our experience is that exchanges like this work much better in person,
where we can bounce ideas around in ways that are hard to replicate in writing.

\item{\bf Project proposal.}
Form a group of between one and three --- no more ---
and choose a single project from those you submitted ---
or perhaps some other idea if you get a sudden flash of inspiration.
Flesh out the project in more detail, {\bf including the data source\/} and
two figures you plan to produce with it.
Total length should be no more than two pages.

On the off-chance you missed the point:  you should {\bf be clear about the data you plan to use\/}.
If you can't get the data, your whole project can be derailed.

{\bf Did we mention data?}

\item {\bf Data report.}
Describe your data and how you accessed it in enough detail that someone else could do it.
Yes, that's ``accessed,'' past tense.  You should have done this already to make sure you have it.
Include your Python code.  % if you read it directly from an internet source.
Internet sources are preferred, because it allows others to use your code and
follow up on your work.

\item {\bf Final project.}
You should submit your {\bf IPython notebook\/} to \href{mailto:db3@nyu.edu}{db3@nyu.edu}
by the due date listed on the course website.
The subject line should be:  ``bootcamp project ug'' or ``bootcamp project mba''
depending on the section you are in.
The file name should be your last names separated by dashes and a short title ---
something like {\tt Jones-Smith-Zhang-India.ipynb}.

Your project should include:
\begin{itemize}
\item Description cell.  Put a Markdown cell at the top of your notebook that
   includes the title of your project, a list of authors, and a short summary
  of what you do.  Think of the last one as an advertisement to potential readers.
\item Data.  Description of data sources and the code to read the data into Python
and reformat it as needed.
This should be done in enough detail that someone else can reproduce what you've done.
\item Graphics.  A series of figures that tell us something interesting.
Three or four would be enough, but do what you think works best for your project.
Think about the narrative:  What story do you want to tell?
\end{itemize}
%We'll post a template.
Here are a few \href{https://github.com/NYUDataBootcamp/Projects}
{past examples}.
\end{itemize}

\section*{Free advice}

Some things to keep in mind:
%
\begin{itemize}
\item {\bf Keep it simple.}
Most project ideas turn out to be too big.  You're generally well-advised
to carve out a manageable subset of what you think you can do.
There's no reason to worry about this at the idea generation stage,
but as you develop your project you may find that you need to focus
more narrowly on a part of it.

\item {\bf Find data.}  Make sure you can get the data you need.
One way to assure this is to start with data and ask what you can do with it.
Ideally you want the intersection (picture a Venn diagram) of an interesting
idea and good data.  You can start with either one, but ideas are often easier to
find than data.
Or start with an existing project that uses data you can access yourself
and extend it in some way.

\item {\bf Ask for help.}
We have years of experience with this kind of thing.
If you're stuck, let us know and we'll try to help.
You can also post questions on the class discussion board.

\end{itemize}

\section*{Grading}

Projects will be graded on their overall quality.  This includes, but is not restricted to,
these categories:
%
\begin{itemize}
\item Quality of the idea.  Is the question clearly articulated?  Is it interesting?
Does it have general appeal?
\item Quality of the data.  Does the data support the idea?
Is it the best data for this question?
\item Degree of difficulty.  Some ideas are harder than others to implement.
As in Olympic diving, you get credit for taking on a challenge.
\item Professional look.  Does your project look professional?  Are the graphs
easy to understand?  Are they clearly labeled?
\end{itemize}

\input{../LaTeX/footer.tex}

%\end{document}
\pagebreak
\thispagestyle{empty}
\input{../LaTeX/header.tex}

\bigskip\bigskip
\centerline{\Large \bf Data Bootcamp:  Project Grade Sheet}
\centerline{Revised: \today}

\section*{Overall}

\begin{itemize} %\itemsep=0.75\bigskipamount
\item Clear idea and message?
\item Appropriate data?
\item Documentation of sources?
\item Effective graphics?
\item Professional appearance?
\end{itemize}
\bigskip

\section*{Idea}

\vspace*{0.75in}

%\begin{itemize} \itemsep=2\bigskipamount
%\item Clarity of the message
%\item ..
%\end{itemize}

\section*{Data}

\vspace*{0.75in}

%\begin{itemize} \itemsep=2\bigskipamount
%\item Clarity of the message
%\item ..
%\end{itemize}

\section*{Graphics}

\vspace*{0.75in}

%\begin{itemize} \itemsep=2\bigskipamount
%\item Clarity of the message
%\item ..
%\end{itemize}

\section*{Difficulty}

\vspace*{0.75in}

%\begin{itemize} \itemsep=2\bigskipamount
%\item Clarity of the message
%\item ..
%\end{itemize}

\section*{Professional look}

\vspace*{0.75in}

%\begin{itemize} \itemsep=2\bigskipamount
%\item Clarity of the message
%\item ..
%\end{itemize}

\input{../LaTeX/footer.tex}

\end{document}

### 2016-09-06 Documents/bootcamp_project_examples.tex
rebuild all text documents to show updated header and date

\documentclass[11pt]{article}

\input{../LaTeX/preamble.tex}

% document starts here
\begin{document}
\parskip=\bigskipamount
\parindent=0.0in
\thispagestyle{empty}
\input{../LaTeX/header.tex}

\bigskip\bigskip
\centerline{\Large \bf Data Bootcamp:  Project Examples}
\centerline{Revised: \today}

\medskip
{\it As always, the pdf of this document comes with links.}

%\medskip
If you're having trouble finding a project idea, here are some you could use or adapt.
Feel free to modify them in any way you find interesting.

\section*{Prepackaged projects}

These are relatively well defined projects that extend things we've done in class.
%
\begin{itemize}
\item {\bf Demographics.\/} Delve deeper into the population dynamics of a country
you find interesting, or compare two or three countries.
You could start with our
\href{https://github.com/NYUDataBootcamp/Materials/blob/master/Code/Lab/UN_demography.ipynb}
{demography notebook},
where we explore UN data on
the age distribution of the population, life expectancy, mortality (deaths), and fertility (births).

One example:  Look at the data for China, see where it leads you.

Another one:  Anne Case and Angus Deaton generated a lot of discussion,
and some controversy, when they documented an increase in mortality of middle-aged white men in the US
and their causes of death, including suicide and drug overdose.
Links:
\href{http://www.nytimes.com/2015/11/03/health/death-rates-rising-for-middle-aged-white-americans-study-finds.html}
    {New York Times},
\href{http://www.nytimes.com/2015/11/07/upshot/more-details-on-rising-mortality-among-middle-aged-whites.html}
    {more Times},
\href{http://www.pnas.org/content/112/49/15078.full.pdf}{Case-Deaton paper} (look at the graphs),
\href{http://andrewgelman.com/wp-content/uploads/2017/04/ageadj.pdf}{Gelman-Auerbach paper} (ditto).
Can you reproduce their work?  Extend it?  Take it in a different direction?

\item {\bf Current economic conditions.\/}  Describe current business conditions in the US.
(Most banks produce this kind of thing, you should be able to find examples.)
This might include:
\begin{itemize}
\item A list of indicators and why you think they're useful.
\item An assessment of the indicators:  either the correlation with industrial production
or some other quantitative measure of how closely it tracks the economy.
\item A summary of what your indicators overall suggest about the current state
of the US economy.
\end{itemize}
Chapter 11 of the \href{(http://www.stern.nyu.edu/experience-stern/about/departments-centers-initiatives/centers-of-research/global-economy-business/development-initiatives/global-economy-course}
{Global Economy book} has a nice overview of what's involved
and FRED codes for some popular indicators.
You can find more indicators --- and descriptions ---
on the
\href{http://www.bloomberg.com/markets/economic-calendar}{Bloomberg economic calendar}.

A variant:  come up with a cool graphic.  We tried a heatmap, but it didn't wow us.
Another idea is a radar chart, like
\href{https://www.frbatlanta.org/chcs/labormarket/}{this one} from the Atlanta Fed.
This requires some serious coding, but the results would be striking.

\item {\bf Emerging market opportunities.\/}  An assessment of
(long-term) business conditions
in emerging market economies.
Here are a couple examples from the Global Economy course:
\href {https://github.com/DaveBackus/Global_Economy/blob/master/Cases/case_foxconn.pdf}
    {Foxconn's Next Frontier}
and \href
    {https://github.com/DaveBackus/Global_Economy/blob/master/Cases/case_ghana.pdf}
    {Opportunity in Ghana}.
In each one, we take a business proposition (start business X)
and assess the relevant aspects of the business climate in two or three countries.
The World Bank's
\href{http://blogs.worldbank.org/opendata/}{Open Data Blog} is a good source of
similar policy-related ideas.

Key data sources for this kind of work:
\begin{itemize}
\item The World Bank's \href{http://data.worldbank.org/}{Open Data Portal} is a good place
to start.  A large collection of social, political and economic data for a broad
range of countries.

\item The World Bank also has (separate) databases related to
\href{http://www.doingbusiness.org/}{Doing Business}
and
\href{http://info.worldbank.org/governance/wgi/index.aspx#home}
{Governance Indicators}.

\item The \href{http://www.rug.nl/research/ggdc/data/pwt/}{Penn World Table}
has data on GDP, employment and hours worked,
and capital.

\item The World Economic Forum does not produce its own data,
but their
\href{http://reports.weforum.org/global-competitiveness-report-2015-2016/}
{Global Competitiveness Report}
has a good summary of information from other sources.
\end{itemize}

\end{itemize}

\section*{Random ideas}

All of these need some work, but they seem promising to us:
\begin{itemize}
\item {\bf Energy prices.\/}
They've dropped a lot, but where will they go from here?  We can think of this in terms of supply and demand.  Demand depends primarily on growth:  higher growth means higher demand.  If China grows more slowly, they’ll demand less.  Supply depends on available resources and technologies to develop new sources --- fracking, for example.  These links focus on supply, which seems to be the central issue right now:
\href{http://ftalphaville.ft.com/2015/09/11/2139891/oil-absolutely-friggin-everywhere/}{Alphaville},
\href{http://econbrowser.com/archives/2014/11/a-glut-of-oil}{Econbrowser}.

\item {\bf Carbon and energy intensity.}
How much energy do countries use?  How much is due to GDP (rich countries use more energy)?  How much to other things?  Can we document the sources of differences in a useful way?  Here are a couple blog posts:
\href{http://conversableeconomist.blogspot.com/2015/07/global-carbon-intensity-rises-kaya.html}
{Conversable},
\href{http://econbrowser.com/archives/2014/06/energy-demand-and-gdp}{Econbrowser}.

\item {\bf How people spend their time.}
The American Time Use Study (ATUS) tells us how people spend every hour of the day.  You can imagine marketing interest in how much time people spend watching TV, accessing the internet, etc.  Many other countries have similar data.  Links:
\href{http://scholar.princeton.edu/sites/default/files/annurev-economics-111809-125129_0.pdf}{survey},
\href{http://www.adweek.com/socialtimes/time-spent-online/613474}{Adweek}, \href{http://www.businessinsider.com/how-much-time-people-spend-online-2013-10}{Business Insider} \href{http://www.nber.org/papers/w19549}{academic paper}, \href{http://www.nielsen.com/us/en/insights/news/2014/whats-empowering-the-new-digital-consumer.html}
{Nielsen}.

\item {\bf Hong Kong/Shanghai share prices (``Hang Seng AH Premium'').}
Shares of some of the same companies are traded in both locations, but at different prices.  Document this over time, showing how the discount on HK shares has varied over time.  Why do you think that is?  Some links:
\href{http://www.hsi.com.hk/HSI-Net/static/revamp/contents/en/dl_centre/factsheets/FS_AHPe.pdf}
{report 1},
\href{http://www.hsi.com.hk/HSI-Net/}{report 2},
\href{http://markets.ft.com/research/Markets/Tearsheets/Summary?s=HSCAHPI:HKG}{FT},
\href{http://www.moneyandbanking.com/commentary/2015/7/6/chinas-stock-market-boom-and-bust}
{Schoenholtz}.

\item {\bf Deflation odds.}
This is moderately technical, but nevertheless interesting.  Inflation-protected government bonds (TIPS) have coupon and principal that are ties to the consumer price index, but there’s a lower bound:  coupon and principal can never go below their issue values.  So if there’s deflation (negative inflation) over the life of the bond, the payments don’t go down.  That gives the bonds an option-like feature that can be used to infer the (risk-adjusted) probability of deflation.  More at the Atlanta Fed:
\href{http://macroblog.typepad.com/macroblog/2015/09/5-year-deflation-probability-moves-off-zero.html}
{blog post},
\href{https://www.frbatlanta.org/research/inflationproject/dp.aspx?d=1&s=blogmb}
{paper}.

\end{itemize}

\section*{Data and package projects}

Here the idea is to describe a dataset or a package.
Why stop there?  Because enough is enough!  But if you do this and still have time
for more, feel free to keep going.
And {\bf if you get stuck, ask for help}.
\begin{itemize}

\item {\bf Describe a package.\/}
Take a package we haven't used and write a tutorial that explains to others how to install
and use it.  Some examples that have come up in class:

\begin{itemize}
\item \href{http://www.crummy.com/software/BeautifulSoup/bs4/doc/}
{Beautiful Soup} ``scrapes''  websites.
The term refers to grabbing data that is posted online but not in a user-friendly format.
We can still grab it with the right tools and a little understanding of the structure
of websites.

\item \href{http://bokeh.pydata.org/en/latest/docs/gallery.html}{Bokeh} does interactive web graphics.
Spencer's a big fan.
One option is to take some graphics we've done in class and redo them in Bokeh,
illustrating its capabilities.

\item \href{https://github.com/quantopian/zipline}{Zipline} is an
``algorithmic trading library.''

\item \href{https://github.com/mrjbq7/ta-lib}{TA-lib}
``performs technical analysis with financial market data.''
\end{itemize}

\item {\bf Describe a dataset.\/}
Take a dataset you find interesting.  Write code that reads it into Pandas
and explain to others how the data might be used.
See the course \href{}{data page}
for examples.
If this sounds insufficiently ambitious, keep in mind that some of these datasets
are pretty complicated.

We have a growing collection of examples, which could serve as your starting point:
\begin{itemize}
\item MEPS.  The Medical Expenditure Panel Survey covers medical expenditures for individuals.
This \href{http://www.nihcm.org/pdf/DataBrief3 Final.pdf}{short report} illustrates its potential.
Figure 1, specifically, shows that 22 percent of total expenditures come
from 1 percent of individuals.
(Think about that for a minute.)
Brian LeBlanc has reproduced this figure from the raw data in an
\href{https://github.com/NYUDataBootcamp/Materials/blob/master/Code/Lab/MEPS_data_experiment_Brian.ipynb}
{IPython notebook}.

\item SCF.  The Fed's Survey of Consumer Finances collects data every three to five years
on household income and (especially) assets and liabilities.
It's a great resource for things like student loan debt, the wealth distribution,
and many other things.
Here's a
\href{http://www.npr.org/sections/money/2015/08/14/431263285/13-years-of-american-credit-cards-in-one-graph}
{nice application}
to credit card debt and interest rates.
\href{https://github.com/NYUDataBootcamp/Materials/blob/master/Code/Lab/SCF_data_experiment_Brian.ipynb}
{Brian LeBlanc's notebook}
shows us the Python code.

\item Airbnb.
Chase likes this collection of \href{http://insideairbnb.com/index.html}{Airbnb data}
and is trying to figure out what to do with it.  If you have ideas, get in touch.

\item {College Scorecard.}
The federal government has posted an enormous collection of material online
about US colleges:  graduation rates, financial aid, salaries after graduation.
Links:  the \href{https://collegescorecard.ed.gov/data/}{data page},
a \href{http://fivethirtyeight.com/features/shut-up-about-harvard/}{538 piece} using the data,
a \href{https://github.com/NYUDataBootcamp/Materials/blob/master/Code/Lab/College_Scorecard_data_input.py}
{Python program} to read in one of the datasets,
and a \href{http://www.vox.com/2015/9/12/9314695/college-scorecard-earnings}{readable overview}.

\end{itemize}

If you have your own ideas, all the better.
Or skim the programs in our
\href{https://docs.google.com/document/d/1L2ZDKFyyqfOrCGbNcCIE9mmgap4tjkTNuw32hK4c6BI/edit?usp=sharing}
{sources and apps} collection.
Or our
\href{https://github.com/NYUDataBootcamp/Lab}{Lab repository}.
(Some of them are works in progress.)

\begin{comment}
\item {\bf IPython notebook of data input chapter.\/}
Create a notebook that goes through the material of the data input chapter of the book,
or perhaps one of the other early chapters.
The result should be a notebook that allows others to teach themselves.
Include blank cells for exercises.
\end{comment}
\end{itemize}

\input{../LaTeX/footer.tex}

\end{document}

### 2016-09-06 Documents/bootcamp_topic_graphics.tex
rebuild all text documents to show updated header and date

\documentclass[11pt]{article}

\input{../LaTeX/preamble.tex}

% document starts here
\begin{document}
\parskip=\bigskipamount
\parindent=0.0in
\thispagestyle{empty}
\input{../LaTeX/header.tex}

\bigskip\bigskip
\centerline{\Large \bf Topic Outline:  Matplotlib Graphics}
\centerline{Revised: \today}

\section*{Materials}

\begin{itemize}
\item  Today's handouts:  this outline, book chapter, code practice answers, stickers (as needed)
\item  All posted on {\it Topic outlines \& links\/} page of website (except the stickers)
\end{itemize}

\section*{Preliminaries}

\begin{itemize}
\item Tools and buzzwords
\begin{itemize}
\item IPython notebooks in Jupyter
\item Graphing with Matplotlib: dataframe plot methods, figure and axis objects
\end{itemize}

\item What is this?
\begin{itemize}
\item Package
\item Pandas
\item {\tt import} statement
\item csv file
\item A dataframe {\tt df}
\item {\tt df.shape}
\item {\tt df.columns}
\item {\tt df.index}
\item Dataframe methods:  \verb|set_index|, {\tt rename}, {\tt drop}
\item The ``x'' and ``y'' variables in the {\tt plot} method
\item Jupyter
\end{itemize}

\item {\bf Exercise}
\begin{itemize}
\item Put red sticker on your laptop

\item Download IPython notebook

%{\small
\url{https://github.com/NYUDataBootcamp/Materials/blob/master/Code/IPython/bootcamp_graphics.ipynb}
%}

and save Raw file in your \verb|Data_Bootcamp| directory

In short:  GitHub $\Rightarrow$ Code $\Rightarrow$ IPython $\Rightarrow$ \verb|bootcamp_graphics.ipynb|
$\Rightarrow$ Raw

\item Start Jupyter and open notebook
\item Run this code:
\begin{verbatim}
import pandas as pd
print('Pandas version: ', pd.__version__)
\end{verbatim}
\item Replace red sticker with green when you're set
\end{itemize}

\needspace{3\baselineskip}
\item {\bf Known issues}
\begin{itemize}
\item Notebook has {\tt .txt} extension.  Solution:  In Jupyter, navigate to the file,
click on the box next to it, click on rename at the top, and delete the extension
{\tt .txt}.
\item Windows 10 + Chrome sometimes has no right-click Save As option.
Solution:  Use a different browser.
\item Some Macs generate the error:  {\tt ValueError: unknown locale: UTF-8.}
Solution:  Ask for help. More at StackOverflow:
\url{http://stackoverflow.com/a/19961403/804513}

\begin{comment}
Or maybe:   
import sys
reload sys
sys.setdefaultencoding('utf-8') 
https://youtu.be/5JnMutdy6Fw?t=43m23s
\end{comment}

\end{itemize}
\end{itemize}

\section*{Python graphics:  Introduction to Matplotlib}

We'll follow the notebook:
\begin{itemize}
\item Jupyter
\item Markdown
\item Preliminaries:  import statements, dataframes to work with
\item Graphing in Excel
\item Apply plot methods to dataframes
\item {\tt plot(x,y)} (skip)
\item Figure and axis objects
\item Recap
\item Bells and whistles
\item Examples
\item Review
\begin{itemize}
\item Put red sticker on, replace with green when done
\end{itemize}
\end{itemize}

\begin{comment}
\section*{Examples}

If time permits, we'll go through some examples of economic and financial data
and its properties.  It's an IPython notebook that you can view on the GitHub repo:
the \verb|Code/IPython| directory,
file \verb|bootcamp_examples.ipynb|.
\end{comment}

\section*{After class}

\begin{itemize}
\item Required
\begin{itemize}
\item Nothing
\end{itemize}
\item Recommended
\begin{itemize}
\item {\bf Write}:  After class, write down everything you remember without using your notes
\item {\bf Review:} Reread the chapter and fill in anything you missed.
\item Download the {\bf Code Practice A} notebook and work through the questions.
If you have trouble with the download step, keep practicing with notebooks
in the {\tt IPython} and {\tt Lab} directories.
You will need this ability for the exam in a few weeks.
\end{itemize}
\end{itemize}

\input{../LaTeX/footer.tex}

\end{document}

### 2016-09-06 Documents/bootcamp_topic_intro.tex
rebuild all text documents to show updated header and date

\documentclass[11pt]{article}

\input{../LaTeX/preamble.tex}

% document starts here
\begin{document}
\parskip=\bigskipamount
\parindent=0.0in
\thispagestyle{empty}
\input{../LaTeX/header.tex}

\bigskip\bigskip
\centerline{\Large \bf Topic Outline:  Data + Python}
\centerline{Revised: \today}

\section*{Materials}

\begin{itemize}
\item  First-day handouts:  Syllabus, Project Guide, Due Dates
\item  Today's handouts:  this outline, three ideas (two copies), book chapters, red/green stickers
\item  All posted on {\it Topic list \& links\/} page of website (except the stickers).
\end{itemize}

\section*{About the course}

\begin{itemize}
\item Data + Python = Magic!
\begin{itemize}
\item Arthur C. Clarke, Jessica, Tim
\end{itemize}

\item What?
\begin{itemize}
\item ... are you doing here?
\item Skills are nice, coding is literacy for the modern age
\item Something to show potential employers
\end{itemize}

\item Why?
\begin{itemize}
\item Why data?
\item Why code?
\item Why Python?
% general purpose language, great data tools, open source and free, community
\item Why bootcamp?
\item Why you?
\end{itemize}

\item Things we believe
\begin{itemize}
\item Anyone can do this.  Target audience is {programming newbies --- with courage}.
\item It's ok to be lost.  We've all been there, it's not permanent.
%\item We're here to help.  But you need to tell us when you're lost.
\item This is fun.  Really.
%It's an amazing feeling to be able to do cool things in minutes.
\end{itemize}

\item Rules to live by
\begin{itemize}
\item Don't panic.  It will seem overwhelming at first, but stick with it and you'll be fine.
\item One step at a time.  Don't rush this.  In six weeks you'll know a lot.
\item Learn by doing.  Same directions as Carnegie Hall, no shortcuts.
%\item Let your nerd flag fly.  Learn to love xkcd.
\item Ask for help.  Don't be a hero, let us know if you could use some help.
\end{itemize}

\needspace{2\baselineskip}
\item Course materials
\begin{itemize}
\item Required:  practice, exam, project
\item Google ``nyu data bootcamp''
\item Website (thanks, Spencer):  \url{http://databootcamp.nyuecon.com/}  (bookmark me!)
\item Book
\item Topic list \& links
\item Discussion group
\item Data page
\item GitHub repository:  \url{https://github.com/NYUDataBootcamp/Materials}
\end{itemize}

\item You
\begin{itemize}
\item Come to class
\item After class:  {\bf write} and {\bf read}
\item Practice
\item Have fun
\end{itemize}
\end{itemize}

\section*{Anaconda}

\begin{itemize}
\item Install the Anaconda distribution
\begin{itemize}
\item Put red sticker on your laptop
\item Distribution?
\item Google ``anaconda download'' or borrow a USB drive
\item Download or copy installer to your computer --- {\bf Python 3.5!}
\item Run installer
\item Start Launcher (use search box)
\item Replace red sticker with green when Launcher opens
\end{itemize}

\item Environments
\begin{itemize}
\item Environments?  (Analogy:  Word is an environment for creating Word docs.)
%(environment is to program as Word is to Word doc)
\item Spyder:  classic coding environment with editor and output windows
\item Jupyter:  environment for creating IPython notebooks, which combine code with text and output
\end{itemize}

\end{itemize}

\section*{Run test program -- twice}

\begin{itemize}
\item Test program code:

\vspace{-0.1in}
\begin{verbatim}
"""
Test program for Data Bootcamp course @ NYU Stern
"""
import sys

print('Welcome to Data Bootcamp!')
print('Python version:')
print(sys.version)
\end{verbatim}

\needspace{2\baselineskip}
\item Run test program in Spyder
\begin{itemize}
\item Put red sticker on your laptop
\item Create \verb|Data_Bootcamp| directory/folder on your computer.
{\bf Raise your hand if you're not sure what that means or how to do it.}
\item From Launcher, launch Spyder (labelled ``spyder-app'')
\item Look around (editor, IPython console, Object inspector)
\item Enter test program in editor (on the left)
\item Save in \verb|Data_Bootcamp| directory as \verb|bootcamp_test.py|
(File, Save as, look for folder)
\item Run program (click on large green triangle)
\item Look for correct output (last line should be {\tt 3.5.x etc})
\item Switch to green sticker if it works
\end{itemize}

\item Run test program in Jupyter
\begin{itemize}
\item Put red sticker on your laptop
\item From Launcher, launch Jupyter (labelled ``ipython-notebook'')
\item Navigate to \verb|Data_Bootcamp| directory
\item Open a new IPython notebook (New, Python 3)
\item Change name from {\tt Untitled} to \verb|bootcamp_test|
\item Look around (toolbar, menubar, code cells)
\item Enter test program in code cell
\item Run program (Cell, Run All)
\item Look for correct output (last line should be {\tt 3.5.x etc})
\item Switch to green sticker if it works
\end{itemize}

\item Spyder startup summary
\begin{itemize}
\item Open by typing Launcher in search box (spotlight on Macs), then choose spyder-app.
\item Or just type Spyder in search box
\end{itemize}

\item GitHub summary
\begin{itemize}
\item Source of course materials
\item Save files by cut and paste, clever save as, or "Raw" (ask about this)
\end{itemize}

\end{itemize}

\section*{Practice and review}

Put red sticker on your laptop, replace with green when you're done.
Discuss with your neighbor.
Raise your hand if you could use some help.

\begin{enumerate}

\item Fill in the blanks in this table:
%relating ``environments'' to the files they are related to:

\begin{center}
\begin{tabular}{cc}
\toprule
Environment & File or Object \\
\midrule
MS Word  & Word document  \\
MS Excel & Excel file     \\
iTunes & \\
%Typewriter & \\
Spyder   &                \\
         & IPython notebook \\
\bottomrule
\end{tabular}
\end{center}

\item Run the \verb|Maddison_data_input.py| Python code example.
\begin{itemize}
\item Go to the \verb|Data_Bootcamp| GitHub repository (link above).
\item Navigate to the {\tt Code} directory and {\tt Lab} subdirectory.
\item Get \verb|Maddison_data_input.py|
\begin{itemize}
\item Cut and paste into blank file
\item Or:  Save file in \verb|Data_Bootcamp| directory (ask how)
\end{itemize}
\item Open file in Spyder (File, Open).
\item Run it by clicking on large green triangle.
\item What do you see?
\end{itemize}

\item {\it Only if you have time.\/} Try this program: \verb|OECD_health_indicators.py|.
What do you see?  What questions does it raise?
(There are other files in the same directory, but some of them don't work yet.)
\end{enumerate}

\section*{Thinking about data}

\begin{itemize}

\item Data + Picture = a compelling way to tell a story

\item Where we're headed
\begin{itemize}
\item Think of a {\bf graph\/} you'd like to produce -- a ``visualization''
\item And the {\bf story\/} it tells
\item And the {\bf data\/} that went into it
\end{itemize}

\item Examples (links on {\it Topic outlines \& links\/} page) [Gapminder]

\item Questions about graphs
\begin{itemize}
\item What did you learn, what is the {\bf story\/}?
\item {\bf What else} would you like to know?
\item Where did the {\bf data\/} come from?
\end{itemize}

\item Examples revisited, answer the questions

\item Course projects
\begin{itemize}
\item Course structure:  tools, project
\item Opportunity to show off your skills (Projects directory of GitHub repo)
\item First step:  develop project ideas ({\bf ideas are developed, not discovered})
\item What interests {you}? (finance? movies?  soccer?)
\end{itemize}

\item Idea machines
\begin{itemize}
\item Start with an idea or subject (what interests you?)
\item Start with a dataset (you'll know more shortly)
\item Start with an example (see link on data page)
\item Start with a suggestion from the people you work with
\end{itemize}

\item Three ideas
\begin{itemize}
\item Put red sticker on your computer
\item Goal:  write down three ideas, 1-2 sentences each (see handout)
\item Use your imagination, don't overthink it (improv: what's your name?)
\item Talk to your neighbors, bounce ideas around
\item Or look at the {\it Data sources\/} page of the course website
\item When you're done, switch to green sticker
\item Share an idea with the class, ask for suggestions for developing further
\item Save ideas for future reference
\item Optional:  leave a copy with me
\end{itemize}
\end{itemize}

\section*{After class}

\begin{itemize}
\item Required
\begin{itemize}
\item Read Syllabus and Project Guide.
\item Mark Due Dates on your calendar.
\item Skim chapters 1-3 of the book.
\end{itemize}
\item Recommended
\begin{itemize}
\item If you haven't already:  join the discussion group, take the entry poll.
\item Explore the website.  Make sure you can find the book, due dates,
topic outlines, assignments, and data sources.
\item Post a link to an interesting graph on the discussion group.
\item Look through the IPython notebook \verb|bootcamp_examples.ipynb|
in the {\tt Code/IPython} directory of the GitHub repo.
What graphs interest you?  What data?
Do they suggest anything else you might explore?
\end{itemize}
\end{itemize}

\input{../LaTeX/footer.tex}

\end{document}

**Outline**

* Why are we doing this?
* Install Anaconda
* Data

**Skills**

Why skills?

* Businesses want people with skills (duh!)

Why code?

* One of the skills businesses value (not the only one)
* Do things Excel can't do, and do them faster

Why Python?

* User-friendly
* Broad range of applications

**Overview**

Where we're headed

* Think of a **picture** you'd like to produce -- a "visualization"
* And about what **data** you'll need
* And the **coding skills** to get there
* Examples:  [Gapminder](http://www.gapminder.org/world/) | [cancer screening](http://www.vox.com/2015/10/28/9631500/does-mammography-work) | [Uber in NYC](http://fivethirtyeight.com/features/uber-is-serving-new-yorks-outer-boroughs-more-than-taxis-are/) | [mortality](http://www.pnas.org/content/early/2015/10/29/1518393112.full.pdf) | [earthquake](https://jawbone.com/blog/napa-earthquake-effect-on-sleep/)

http://graphics.wsj.com/infectious-diseases-and-vaccines/

http://www.nytimes.com/interactive/2016/01/07/us/drug-overdose-deaths-in-the-us.html

Philosophy

* Target **coding novices**, no prior experience required or expected
* **Jump right in** the deep end of the pool, figure it out as we go
* Not a typical programming course:  cover only those aspects of Python relevant to data work

Rules to live by

* **Don't panic**.  The jargon and concepts will seem mysterious at first, but if you keep with it they'll start to make sense.
* **One step at a time.**  We'll go as slowly as we need.  Speed is the enemy, it leads to mistakes.
* **Doing is learning.**  We'll set you up to teach yourself.  If you're stuck, either **ask for help** or practice your **Google fu** and find the answer with Google.

**Prelaunch checklist**

Install Anaconda

* Google "anaconda download"
* Download installer for **Python 3.5**
* Run installer

Locate this file in a browser

* Google "nyu data bootcamp" and follow links
* Or:  type in url at the top

Save today's code file in a handy place

* Create directory/folder \verb|Data_Bootcamp|
* Click on code link above, then Raw button
* Save file in `Data_Bootcamp` directory

Launch

* Look for **Launcher** in your programs
* Start it up (takes a minute)
* Click on **Spyder** (another minute)

\input{../LaTeX/footer.tex}

\end{document}

### 2016-09-06 Code/Python/bootcamp_examples.py
updated all links in .py files

@@ -7,7 +7,7 @@ off the web access tools into a new package.
 http://pandas.pydata.org/pandas-docs/stable/remote_data.html
 
 Repository of materials (including this file):
-* https://github.com/DaveBackus/Data_Bootcamp
+* https://github.com/NYUDataBootcamp/Materials
 
 Written by Dave Backus, November 2015
 Created with Python 3.5

### 2016-09-06 Code/Python/bootcamp_fundamentals_2.py

@@ -3,7 +3,7 @@ Python fundamentals, part 2, for Data Bootcamp course.
 
 Course materials
 * http://databootcamp.nyuecon.com/
-* https://github.com/DaveBackus/Data_Bootcamp
+* https://github.com/NYUDataBootcamp/Materials
 
 Warning:  This is a working file and has some things in it that aren't
 completely debugged.

### 2016-09-06 Code/Python/bootcamp_graphics_1.py

@@ -10,7 +10,7 @@ Graphics inherently complicated, see these options to get a sense:
 http://matplotlib.org/users/customizing.html
 
 Repository of materials (including this file):
-* https://github.com/DaveBackus/Data_Bootcamp
+* https://github.com/NYUDataBootcamp/Materials
 
 Written by Dave Backus, August 2015
 Created with Python 3.5

### 2016-09-06 Code/Python/bootcamp_pandas_2.py

@@ -4,8 +4,8 @@ Pandas advanced tools for Data Bootcamp course.
 Topics:  reading csv and xls files, properties of dataframes.
 
 Repository of materials (including this file):
-* https://github.com/DaveBackus/Data_Bootcamp
-* https://github.com/DaveBackus/Data_Bootcamp/Code/Python
+* https://github.com/NYUDataBootcamp/Materials
+* https://github.com/NYUDataBootcamp/Materials/Code/Python
 
 Written by Dave Backus, August 2015
 Created with Python 3.4
@@ -123,8 +123,8 @@ most are for the WDI, which is way too big and takes too long
 # copy file from url to hard drive
 import urllib.request           # this is a module from the package urllib
 file = 'foo.csv'
-url1 = 'https://raw.githubusercontent.com/DaveBackus/Data_Bootcamp/master/'
-url2 = 'Code/Data/test1.csv'
+url1 = 'https://raw.githubusercontent.com/NYUDataBootcamp/Materials/master/'
+url2 = 'Data/test.csv'
 url = url1 + url2
 urllib.request.urlretrieve(url, file)
 

### 2016-09-06 Documents/bootcamp_syllabus.tex
updated syllabus

@@
 The {\bf book\/} has its own site,
-% TODO: We need to change this link once gitbook is re-enabled
 \vspace{-0.15in}
 \begin{center}
-\url{https://www.gitbook.com/book/davebackus/test/details}
+\url{https://www.gitbook.com/book/nyudatabootcamp/data-bootcamp/details}
 \end{center}
@@
 The links are
-% TODO: we need to update these links once we decide where our forum will go
 \vspace{-0.1in}
@@
 are due at the start of class on the specified dates.
+
 {\bf Dates are not negotiable.
@@
 \end{center}
+
 Final grades are not subject to any fixed distribution or curve.
@@
 \item {\it Write:\/}  Shortly after class, write down everything you remember
-without looking at your notes or the book.
-Note things you don't understand --- gaps, we call them.
-\item {\it Review:\/} Read the relevant section of the book.  Fill in the gaps.
-Ask for help with anything you still don't understand.
+without looking at your notes or the book. Note things you don't understand --- gaps, we call them.
+\item {\it Review:\/} Read the relevant section of the book.  Fill in the gaps. Ask for help with anything you still don't understand.
 %\item {\bf Review:\/} Later on, go through what you wrote down earlier and  fill in the gaps
@@
 
-% TODO: we need to fix the email address below once we finish setting up the domain
 You can find answers to common questions on the course website.
@@
 212-998-4980) and ask them to
-send me a letter verifying your registration and outlining the accommodation they recommend.
+send us a letter verifying your registration and outlining the accommodation they recommend.
 If you need to take an exam at the CSD,
@@
 \end{document}
-
-OLD STUFF
-
-\begin{itemize}
-\item Data. We live in a world that's ...
-\item Programming. To make sense of the data, you need to be able to code:
-to write computer programs to put the data in a form that ...
-Be forwarned:  you are expected to write programs in this course.
-This can be incredibly frustrating and requires enormous patience.
-If that's not your thing, you should not take this course.
-\item Graphics.
-\end{itemize}

### 2016-09-06 Documents/bootcamp_topic_pandas-clean-shape.tex
rebuild all text documents to show updated header and date (#10)

\documentclass[11pt]{article}

\input{../LaTeX/preamble.tex}

% document starts here
\begin{document}
\parskip=\bigskipamount
\parindent=0.0in
\thispagestyle{empty}
\input{../LaTeX/header.tex}

\bigskip\bigskip
\centerline{\Large \bf Topic Outline:  Cleaning \& Shaping Data}
\centerline{Revised: \today}

\section*{Materials}

\begin{itemize}
\item  Today's handout:  this outline
\item  Posted on {\it Topic outlines \& links\/} page of website
\end{itemize}

\section*{Our approach to the second half of the course}

\begin{itemize}
\item Cover things you're likely to find useful 
\item Think of it as a menu:  choose what you like 
\item {\bf Ask for help} if you're stuck, either in class or on your project
\item We'll work applications and short topics into the flow
\end{itemize}

\section*{Current plan}

Here's the current plan, but we welcome comments and suggestions.
The topics at the end are maybes, they depend on interest and time.
\begin{itemize}
\item Advanced data management with Pandas
\begin{itemize}
\item Data cleaning:  fixing numbers treated as strings,
selecting rows and columns, Boolean selection
\item Data shaping:  switching rows and columns, pivoting, indexing
\item Merging datasets:  combining information from different dataframes/worksheets
\item Summarizing data:  statistics (mean, standard deviation), grouping observations
\end{itemize}

\item Updating and installing Python and packages
\begin{itemize}
\item Conda and Pip
\end{itemize}

\item Advanced graphics
\begin{itemize}
\item Packages:  Seaborn and Plotly
\item Applications:  maps, animations
\end{itemize}

\item Web scraping
\begin{itemize}
\item Grabbing data from websites that are not designed for it
\item Package:  Beautiful Soup
\item Problem:  not easy to do if you don't understand the language of websites (html)
\end{itemize}

\item Distribution, dependence, and dynamics
\begin{itemize}
\item The mean isn't enough, we want to know the range of outcomes.
\item Distribution is about outcomes:  equity returns, options, individual incomes, many more.
Graphical methods for identifying the ``long tail.''
\item Dependence is about the relation between two variables, often summarized by correlation.
\item Dynamics is about dependence over time:  Are good times followed by good times, or the opposite?
Examples:  equity returns, economic growth, bond ratings.
\end{itemize}

\item Overview of statistics and machine learning tools in Python
\begin{itemize}
\item Big topics, this will be superficial (but possibly useful)
\item Packages:  StatsModels and Scikit-Learn
\end{itemize}

\end{itemize}

\section*{Pandas 2:  Data cleaning}

\begin{itemize}
\item Setup
\begin{itemize}
\item Download IPython notebook

%{\small
\url{https://github.com/NYUDataBootcamp/Materials/blob/master/Code/IPython/bootcamp_pandas-clean.ipynb}
%}

and save Raw file in your \verb|Data_Bootcamp| directory

In short:  GitHub $\Rightarrow$ Code $\Rightarrow$ IPython $\Rightarrow$
 \verb|bootcamp_pandas-clean.ipynb| $\Rightarrow$ Raw

\item Open in Jupyter
\end{itemize}

\item {\bf Want operator}
\begin{itemize}
\item Keep in mind what we want, then figure out how to get there
\item Problems:  numbers contain dollar signs or commas, interpreted as strings;
missing values not marked;
dataset contains a lot of stuff we don't want; rows and columns are flipped.
\end{itemize}

\item String methods
\begin{itemize}
\item Fixing oddities in data:  dollar signs, commas, etc.
\end{itemize}

\item Missing values
\begin{itemize}
\item Identify missing values, then Pandas will automatically work around them
\end{itemize}

\item Selecting variables (columns) and observations (rows)
\begin{itemize}
\item Various things we don't use much
\end{itemize}

\item Boolean selection
\begin{itemize}
\item Things we use
\item Comparisons, boolean selection, the {\tt isin} method
\end{itemize}

\end{itemize}

\section*{Pandas 3:  Data shaping}

\begin{itemize}
\item Setup
\begin{itemize}
\item Download IPython notebook

%{\small
\url{https://github.com/NYUDataBootcamp/Materials/blob/master/Code/IPython/bootcamp_pandas-shape.ipynb}
%}

and save Raw file in your \verb|Data_Bootcamp| directory

In short:  GitHub $\Rightarrow$ Code $\Rightarrow$ IPython $\Rightarrow$
 \verb|bootcamp_pandas-shape.ipynb| $\Rightarrow$ Raw

\item Open in Jupyter
\end{itemize}

\item Want operator
\begin{itemize}
\item Problem:  Rows and columns are switched, or worse
\end{itemize}

\item Setting and resetting the index
\item Multi-indexes
\item Switching rows and columns, pivoting
\item Stacking and unstacking:  the components of pivoting
\end{itemize}

\section*{After class}

\begin{itemize}
\item Required
\begin{itemize}
\item Submit Revised Project Ideas
\end{itemize}
\item Recommended
\begin{itemize}
\item Skim Project Guide
\item Skim Project Examples
\item Bounce around project ideas with friends
\end{itemize}
\end{itemize}

\input{../LaTeX/footer.tex}

\end{document}

### 2016-09-06 Documents/bootcamp_topic_pandas-clean.tex
rebuild all text documents to show updated header and date (#10)

--- 2016-09-06 Documents/bootcamp_topic_pandas-clean-shape.tex
@@
 \bigskip\bigskip
-\centerline{\Large \bf Topic Outline:  Cleaning \& Shaping Data}
+\centerline{\Large \bf Topic Outline:  Cleaning Data}
 \centerline{Revised: \today}
@@
 \item Keep in mind what we want, then figure out how to get there
-\item Problems:  numbers contain dollar signs or commas, interpreted as strings;
+\item Examples:  numbers contain dollar signs or commas, interpreted as strings;
 missing values not marked;
@@
 \begin{itemize}
-\item Things we use
-\item Comparisons, boolean selection, the {\tt isin} method
+\item Things we use --- a lot
+\item Comparisons, boolean selection
+\item The {\tt isin} and {\tt contains} methods
 \end{itemize}
 
-\end{itemize}
-
-\section*{Pandas 3:  Data shaping}
-
-\begin{itemize}
-\item Setup
-\begin{itemize}
-\item Download IPython notebook
-
-%{\small
-\url{https://github.com/NYUDataBootcamp/Materials/blob/master/Code/IPython/bootcamp_pandas-shape.ipynb}
-%}
-
-and save Raw file in your \verb|Data_Bootcamp| directory
-
-In short:  GitHub $\Rightarrow$ Code $\Rightarrow$ IPython $\Rightarrow$
- \verb|bootcamp_pandas-shape.ipynb| $\Rightarrow$ Raw
-
-\item Open in Jupyter
-\end{itemize}
-
-\item Want operator
-\begin{itemize}
-\item Problem:  Rows and columns are switched, or worse
-\end{itemize}
-
-\item Setting and resetting the index
-\item Multi-indexes
-\item Switching rows and columns, pivoting
-\item Stacking and unstacking:  the components of pivoting
 \end{itemize}

### 2016-09-06 Documents/bootcamp_topic_review.tex
rebuild all text documents to show updated header and date (#10)

\documentclass[11pt]{article}

\input{../LaTeX/preamble.tex}

% document starts here
\begin{document}
\parskip=\bigskipamount
\parindent=0.0in
\thispagestyle{empty}
\input{../LaTeX/header.tex}

\bigskip\bigskip
\centerline{\Large \bf Topic Outline:  Review \& Applications}
\centerline{Revised: \today}

\section*{Materials}

\begin{itemize}
\item  Today's handouts:  this outline, stickers (as needed)
\item  Posted on {\it Topic outlines \& links\/} page of website (except the stickers)
\end{itemize}

\section*{Preliminaries}

\begin{itemize}
\item Next week's exam
\begin{itemize}
\item Covers:  Python fundamentals 1/2, data input with Pandas, graphics with Matplotlib
\item Like a driving test:  just the essentials
\item Format:  an IPython notebook like the one we use below.  Add answers, email it back to us.
\item Rules:  open book and open internet (wireless permitting), but we recommend a one-page ``cheat sheet''
\end{itemize}

\item {\bf Exercise (review setup)}
\begin{itemize}
\item Put red sticker on your laptop

\item Download IPython notebook

%{\small
\url{https://github.com/NYUDataBootcamp/Materials/blob/master/Code/IPython/bootcamp_exam_practice.ipynb} %}

and save Raw file in your \verb|Data_Bootcamp| directory

In short:  GitHub $\Rightarrow$ Code $\Rightarrow$ IPython $\Rightarrow$ \verb|bootcamp_exam_practice.ipynb|
$\Rightarrow$ Raw

\item {\bf We're going to start Jupyter without using Launcher}
\item Go to the command line
\begin{itemize}
\item Windows:  push the Windows key and enter "command prompt".
\item Macs:  click the magnifying glass in the top right and enter "terminal".
\end{itemize}
\item Type:  jupyter notebook [enter]
\item If this starts Jupyter, you're all set.  {\bf If not, let us know.}
\item Replace red sticker with green when you're set
\end{itemize}

%\needspace{3\baselineskip}
\end{itemize}

\section*{Exam practice}

Work your way through the practice exam.  Raise your hand when you get stuck.
\begin{itemize}
\item IPython basics
\item Python fundamentals
\item Data input with Pandas
\item Graphics with Matplotlib
\end{itemize}

\section*{Applications}

{\bf Setup}
\begin{itemize}
\item Put red sticker on your laptop

\item Download IPython notebook

%{\small
\url{https://github.com/NYUDataBootcamp/Materials/blob/master/Code/IPython/bootcamp_examples.ipynb} %}

and save Raw file in your \verb|Data_Bootcamp| directory

In short:  GitHub $\Rightarrow$ Code $\Rightarrow$ Lab $\Rightarrow$ \verb|UN_demography.ipynb|
$\Rightarrow$ Raw

\item Start Jupyter -- {\bf from the command line} -- and open notebook
\item Replace red sticker with green when you're set
\end{itemize}

{\bf Demography.} 
We'll spend the rest of the class looking at demographic data.
We do this partly because it's inherently interesting,
partly because it's a good illustration of the research process:
We start with one fact, which suggests followup questions
that drive us to look for other facts,
Repeat as needed.

The code here goes beyond what we've done so far.  
We'll fill that in later, but feel free to ask questions
as we go. 
Topic list:   
\begin{itemize}
\item Aging populations (esp Japan)
\item Fertility (births)
\item Life expectancy
\item Mortality (deaths)
\end{itemize}

\section*{After class}

\begin{itemize}
\item Required
\begin{itemize}
\item Nothing
\end{itemize}
\item Recommended
\begin{itemize}
\item Review book chapters
\item Review code practice
\item Prepare your cheat sheet
\end{itemize}
\end{itemize}

\input{../LaTeX/footer.tex}

\end{document}

### 2016-09-06 Documents/bootcamp_project.tex
Update to project pdf.

@@
 to demonstrate your data and programming skills to potential employers.
-That work will come in the form of an IPython/Jupyter notebook,
+That work will come in the form of a Jupyter notebook,
 a format that combines code, text, and graphics in one user-friendly document.
@@
 Data Report                 & Paper (professional)  & Group       & 5  \\
-Final Project               & IPython/Jupyter notebook      & Group       & 85 \\
+Final Project               & Jupyter notebook      & Group       & 85 \\
 \bottomrule
@@
 \item {\bf Final project.}
-You should submit your {\bf IPython notebook\/} to \href{mailto:db3@nyu.edu}{db3@nyu.edu}
+You should submit your {\bf Jupyter notebook\/} to \href{mailto:nyu.databootcamp@gmail.com}{nyu.databootcamp@gmail.com}
 by the due date listed on the course website.
@@
 Is it the best data for this question?
+\item Quality of the code. Is the code readable? Could someone else understand what you were doing and why?
 \item Degree of difficulty.  Some ideas are harder than others to implement.

### 2016-10-04 Code/Python/bootcamp_pandas-input.py
added debate csv example to pandasinput.py

@@ -5,12 +5,11 @@ Course materials
 * http://databootcamp.nyuecon.com/
 * https://github.com/NYUDataBootcamp/Materials
 
-Warning:  This is a working file and has some things in it that aren't
-completely debugged.
-
 Written by Dave Backus, August 2015
 Created with Python 3.4
 """
+
+#%%
 """
 Read csv file from internet (and why we like csv's)
 The result is a data frame:  like a sheet with row and column labels
@@ -26,6 +25,23 @@ df = pd.read_csv(url)
 # if the internet is down
 #df_fromdict = pd.DataFrame({'name': ['Dave', 'Chase', 'Spencer'],
 #            'x1': [1, 4, 5], 'x2': [2, 3, 6], 'x3': [3.5, 4.3, 7.8]})
+
+
+#%%
+
+# windows users only
+# folder = "\C:\Users"  # WILL NOT WORK
+folder = "\\C:\\Users"  # Good
+folder = "/C:/Users"  # Good
+
+
+
+
+
+folder = "/Users/sglyon/Teaching/NYUDataBootcamp/Materials/Data/"
+csv_file = folder + "test.csv"
+df = pd.read_csv(csv_file)
+
 
 #%%
 """
@@ -84,8 +100,24 @@ df538["Median"].plot(kind="barh", figsize=(5, 12))
 
 #%%
 # IMDb movies and parts
+# WARNING: this file is approx 200 MB -- this might take a while
 url  = 'http://pages.stern.nyu.edu/~dbackus/Data/cast.csv'
 cast = pd.read_csv(url, encoding='utf-8')
+
+#%% first 2016 presdidential debate
+# NOTE: data came from here: 
+# https://www.kaggle.com/mrisdal/2016-us-presidential-debates
+url1 = "https://raw.githubusercontent.com/NYUDataBootcamp/Materials/"
+url2 = "master/Data/pres_debate_2016.csv"
+url= url1 + url2
+debate = pd.read_csv(url)
+
+# who spoke more
+trump = debate[debate["Speaker"] == "Trump"]
+clinton = debate[debate["Speaker"] == "Clinton"]
+
+print("Length of Trumps's talking ", len(trump["Text"].sum()))
+print("Length of Clinton's talking ", len(clinton["Text"].sum()))
 
 #%%
 """

### 2016-10-05 Documents/bootcamp_practice_3.tex
updated HW 3

@@
 \item What type of object is \texttt{weo['BRA']}?
-\item Create a new variable equal to the ratio of Brazil's GDP per capita to Japan's.
+\item Create a new variable equal to the ratio of Brazil's GDP per capita to Japan's and add it to the DataFrame.
 \item {\it Challenging.\/}
@@
 \vspace{0.1in}
-\centerline{\url{http://pages.stern.nyu.edu/~dbackus/Data/Data-Bootcamp-entry-poll_s16.csv}}
+\centerline{\url{https://raw.githubusercontent.com/NYUDataBootcamp/Materials/master/Data/entry_poll_fall16.csv}}
 \vspace{0.1in}

### 2016-10-06 Documents/bootcamp_syllabus.tex
Small changes to syllabus -- Add words about code practice and project. (#15)

@@
 We encourage you do to all of them --- they're good practice ---
-but your grade will be based on the best two.
+but your grade will be based on the best two. We find that people who finish these assignments
+tend to keep up with the material better and these are easy points to get in terms of grades.
 We will also distribute Optional Code Practice ``assignments,''
@@
 that you can share with potential employers.
-The structure of the project is laid out in a separate document.
+The structure of the project is laid out in a separate document. We have found that the quality
+of final project had a surprisingly low correlation to previous programming experience. A little thought and
+effort go a long way in creating an interesting project.
 

### 2016-10-25 Documents/bootcamp_pyfun_review_answers.md
Add answers to review.

# Python Fundamentals Review

In this file, we will review all of the material that has been covered in "Python Fundamentals 1" and "Python Fundamentals 2." This is _not_ for a grade and is meant to be used as a checkpoint for yourself.

The material covered in this review (and in the Python Fundamentals sections) is foundational. If you have questions, please ask. It will be important to understand this material for the rest of this course. Some of these are meant to be a little challenging to stretch you -- If there are problems that you can't do, don't despair -- Instead of getting worried, ask questions! As if we haven't said this enough times: IF YOU NEED HELP, PLEASE ASK QUESTIONS!!!

## Types

We have discussed various types that are used within Python. This section will ask you about these types. For each question with multiple answers, circle all of the types that apply.

1. Which of the following are numerical types
  - string
  - list
  - int (Yes)
  - float (Yes)
  - tuple
  - dictionary
  - bool

2. Which of the following would you typically use to store text?
  - string (Yes)
  - list
  - int
  - float
  - tuple
  - dictionary
  - bool

3. Which of the following would you use to store keys and values?
  - string
  - list
  - int
  - float
  - tuple
  - dictionary (Yes)
  - bool

4. Which of the following would you use to store items that you wanted to iterate over?
  - string (Yes)
  - list (Yes)
  - int
  - float
  - tuple (Yes)
  - dictionary (Yes)
  - bool

5. What do each of the following types do when they are multiplied by 2?
  - string (concatenates string together twice --> `"abc"*2 => "abcabc"`
  - list (concatentates lists together twice --> `[1, 2]*2 => [1, 2, 1, 2]`
  - int (double the integer)
  - float (doubles the float)
  - tuple (error)
  - dictionary (error)
  - bool (returns 2 if true and 0 if false)

6. What is the type and value of each of the following commands? If you don't know, can you think of a way to find out?
  - `2 * 3` (Int)
  - `2 * 3.0` (Float)
  - `"abc" * 3` (string)
  - `list("abc") * 2` (list)
  - `str(int(float("12.34")))` (string)
  - `[1, 2, 3] + ["one", "two", "three"]` (list)
  - `dict(zip([1, 2, 3], ["one", "two", "three"]))` (dictionary)
  - `1 > 0` (boolean)
  - `1 < 0` (boolean)

7. What do we mean when we talk about "tab completion" for a type? We are referring to the fact that after typing an object `x` we can type a `.` and then hit tab to reveal all of its corresponding methods

## Writing python code and using Spyder

The information covered in this section is probably a bit less "fundamental" than what was covered in the previous section, but knowing the answers to this section can help you write your code more efficiently.

8. What is Spyder? The environment that we have used for programming so far

9. How do you open Spyder? Open a terminal and type `spyder`

10. How could you find out more information about a function in Spyder? For example, if you wanted to know more about the `print` function where could you find that information? Type `print?` in the ipython terminal or search in object inspector

11. What is it when you leave notes to yourself within your code? How do you make these notes? A comment -- We leave them using `#`

12. What is a cell block and how do we make one? How do we run only a single block at a time? How would we run an entire file at once? We create cell blocks with `#%%`. We can run one at a time using `Ctrl+Enter`. We can run an entire file by clicking green arrow at top

13. How do we change our "working directory" to the data bootcamp folder? Use upper right corner folder

## Practice problems

These are practice problems that apply the concepts we have discussed so far

14. Suppose that we borrow 200 for one year at an interest rate of 5 percent. If we pay interest plus principal at the end of the year, what is our total payment? Compute this using variables `principal` and `i` (for interest rate). Print your answer.

```python
principal = 200
i = 0.05
print(principal * (1 + i))
```

15. Imagine that now you wanted to compute the interest plus principal for multiple interest rates. How would you store multiple interest rates? Now print the answer for a principal of 200 and interest rates of 1, 2, 5, and 10 percent (Hint: easiest way is to do this in a loop).

```python
i_values = [0.01, 0.02, 0.05, 0.10]
principal = 200

for ir in i_values:
    print(principal * (1 + ir)
```

16. (Challenging) This will be your first chance at doing "text analysis" in this course. Enter the code below into Python. It is a poem by Edgar Allan Poe. It is secretly dedicated to Poe's friend. The name is written by taking one letter from each line -- In particular, if you are on line i then use the ith letter (if you were on line 7 then you would use the 7th letter, not including spaces, which is s). Your job is to print the name of his friend (letter by letter is fine) that it was dedicated to. I will give two hints: use the string method for splitting (either `.split(/n)` or `.splitlines()`) to break the code up into lines and then the second hint is that you will want to ignore the spaces and punctuation (find a string method that you can use get rid of them).

```python
txt = """For her this rhyme is penned, whose luminous eyes,
Brightly expressive as the twins of Loeda.
Shall find her own sweet name, that, nestling lies
Upon, the page, enwrapped from every reader.
Search narrowly the lines! — they hold a treasure
Divine—a talisman—an amulet
That must be worn at heart. Search well the measure
The words—the syllables! Do not forget
The trivialest point, or you may lose your labor!
And yet there is in this no Gordian knot
Which one might not undo without a saber,
If one could merely comprehend the plot.
Enwritten upon the leaf where now are peering
Eyes scintillating soul, there lies perdus
Three eloquent words oft uttered in the hearing
Of poets, by poets as the name is a poet's, too.
Its letters, although naturally lying
Like the knight Pinto—Mendez Ferdinando
Still form a synonym for Truth. Cease trying!
You will not read the riddle, though you do the best you can do."""

punctuation = [" ", ",", "!", "-", "."]
for p in punctuation:
    txt = txt.replace(p, "")

name = ""
lines = txt.splitlines()
for i in range(len(lines)):
    name = name + lines[i][i]

print(name)
```

17. Sum all of the numbers less than 200. What is the value?

```python
total = 0.0
for i in range(200):
    total = total + i

print("The value is", total)
```

18. Create a list that computes the cumulative sum from 0 to 10 (not including 10). The answer should be `[ 0,  1,  3,  6, 10, 15, 21, 28, 36, 45]`. Save this list as `cs` which we will use in the next couple problems.

```python
total = 0
cs = []
for i in range(10):
    total = total + i
    cs.append(total)
```

19. How would you get the 4th element (6) from `cs`?

```python
print(cs[3])
```

20. How would you get the first 4 elements from `cs`?

```python
print(cs[:4])
```

21. How would you get the last 4 elements from `cs`?

```python
print(cs[-4:])
```

22. Write a function which takes a first name and last name and returns the combination of the names. For example, if `firstname = "Chase"` and `lastname = "Coleman"` then the function should return `"Chase Coleman"`.

```python
def combine_names(first, last):
    return first + " " + last
```

23. Write a function which takes two first names and returns the names in alphabetical order. For example, if `name1 = "Chase"` and `name2 = "Chad"` then the function should return `("Chad", "Chase")`.

```python
def order_names(name1, name2):
    if name1 < name2:
        return (name1, name2)
    else:
        return (name2, name1)
```

24. Take the list of growth rates `g = [0.02, 0.07, 0.08]`. Write a list comprehension that multiplies each element by 100. Do the same exercise by using a loop and storing them in a new list.

```python
g = [0.02, 0.07, 0.08]
g_p = [gi*100 for gi in g]
```

25. Think about everything we've done so far. If you have questions, raise your hand or write an email to us. ASK QUESTIONS.

:)

### 2016-10-26 Code/Python/bootcamp_pandas-intro.py
Make corresponding changes from lecture to python files.

@@ -1,0 +1,89 @@
+"""
+Pandas introduction for Data Bootcamp course.
+
+Course materials
+* http://databootcamp.nyuecon.com/
+* https://github.com/NYUDataBootcamp/Materials
+
+Written by Chase Coleman, October 2016
+Created with Python 3.5
+"""
+
+#%%
+# We will always import pandas as pd -- This is more or less a
+# convention across the data community
+import pandas as pd
+
+#%%
+# This dictionary is similar to one that we saw earlier in the class
+# It represents GDP/CPI data at 10 year intervals from 1990 to 2010
+df = pd.DataFrame({"GDP": [5974.7, 10031.0, 14681.1],
+                   "CPI": [127.5, 169.3, 217.488],
+                   "Year": [1990, 2000, 2010],
+                   "Country": ["US", "US", "US"]})
+print(df)
+print(type(df))
+
+#%%
+
+dft = df.T
+print("\n", dft)
+
+#%%
+# This is for exercise!!!
+data = {'countrycode': ['CHN', 'CHN', 'CHN', 'FRA', 'FRA', 'FRA'],
+        'pop': [1124.8, 1246.8, 1318.2, 58.2, 60.8, 64.7],
+        'rgdpe': [2.611, 4.951, 11.106, 1.294, 1.753, 2.032],
+        'year': [1990, 2000, 2010, 1990, 2000, 2010]}
+pwt = pd.DataFrame(data)
+
+# Fill in your answers below
+
+#%%
+
+print(df["GDP"])
+print(type(df["GDP"]))
+
+#%%
+print(df["GDP"] + df["GDP"])
+print(df["GDP"] - df["GDP"])
+print(df["GDP"] / df["CPI"])
+print(df["CPI"] * df["CPI"])
+print(df["GDP"] / 10000)
+
+#%%
+df['RGDP'] = df['GDP']/df['CPI']
+df['GDP_div_1000'] = df['GDP'] / 1000
+
+#%%
+
+df.columns = ["cpi", "country", "gdp", "year", "rgdp", "gdp_div_1000"]
+
+# Could also use
+df.columns = [var.lower() for var in df.columns]
+# or
+df = df.rename(columns={"gdp": "ngdp"})
+
+#%%
+namelist = ['ngdp', 'rgdp']
+numlist  = [2, 4]
+df_v1 = df[namelist]
+df_v2 = df[numlist]
+
+#%%
+
[…]

### 2016-10-26 Code/Python/bootcamp_pandas-input.py
Make corresponding changes from lecture to python files. (#24)

@@ -7,6 +7,9 @@ Course materials
 
 Written by Dave Backus, August 2015
 Created with Python 3.4
+
+Edited by Chase Coleman and Spencer Lyon, October 2016
+Created with Python 3.5
 """
 
 #%%
@@ -35,9 +38,7 @@ folder = "\\C:\\Users"  # Good
 folder = "/C:/Users"  # Good
 
 
-
-
-
+# NEED TO CHANGE TO YOUR OWN PATH HERE
 folder = "/Users/sglyon/Teaching/NYUDataBootcamp/Materials/Data/"
 csv_file = folder + "test.csv"
 df = pd.read_csv(csv_file)
@@ -105,7 +106,7 @@ url  = 'http://pages.stern.nyu.edu/~dbackus/Data/cast.csv'
 cast = pd.read_csv(url, encoding='utf-8')
 
 #%% first 2016 presdidential debate
-# NOTE: data came from here: 
+# NOTE: data came from here:
 # https://www.kaggle.com/mrisdal/2016-us-presidential-debates
 url1 = "https://raw.githubusercontent.com/NYUDataBootcamp/Materials/"
 url2 = "master/Data/pres_debate_2016.csv"
@@ -123,19 +124,19 @@ print("Length of Clinton's talking ", len(clinton["Text"].sum()))
 """
 APIs
 """
-import pandas.io.data as web    # package to access FRED
-import datetime as dt           # package to handle dates
+from pandas_datareader import data  # Package to access FRED
+import datetime as dt               # package to handle dates
 
 start = dt.datetime(2010, 1, 1)  # start date
-codes = ['GDPC1', 'PCECC96']    # real GDP, real consumption
-fred  = web.DataReader(codes, 'fred', start)
-fred = fred/1000                # convert trillions to billions
+codes = ['GDPC1', 'PCECC96']     # real GDP, real consumption
+fred  = data.DataReader(codes, 'fred', start)
+fred = fred/1000                # convert billions to trillions
 
 fred.plot()
 
 #%%
 # World Bank
-from pandas.io import wb            # World Bank api
+from pandas_datareader import wb   # World Bank api
 
 var = ['NY.GDP.PCAP.PP.KD']         # GDP per capita
 iso = ['USA', 'FRA', 'JPN', 'CHN', 'IND', 'BRA', 'MEX']  # country codes
[…]

### 2017-02-07 Code/Python/pract_fund1_sol.py
add pyfund1_sol

@@ -1,0 +1,110 @@
+"""
+Practice problems, Python fundamentals 1 -- Solutions
+
+@authors: Balint Szoke, Daniel Csaba
+@date: 06/02/2017
+"""
+
+#-------------------------------------------------------  
+# 1) Solution
+good_string = "Sarah's code"
+#or 
+good_string = """Sarah's code"""
+ 
+#-------------------------------------------------------  
+# 2) Solution
+i = 1234
+list(str(i))
+
+#-------------------------------------------------------  
+# 3) Solution
+year = '2016'
+next_year = str(int(year) + 1)
+
+#-------------------------------------------------------  
+# 4) Solution
+x, y = 3, 'hello'
+print(x, y)
+z = x
+x = y
+y = z
+print(x, y)
+
+#-------------------------------------------------------  
+# 5) Solution
+name = 'Jones'
+print(name.upper())
+
+#-------------------------------------------------------  
+# 6) Solution
+name = 'Ulysses'
+print(name.count('s'))
+
+#-------------------------------------------------------  
+# 7) Solution
+long_string = 'salamandroid'
+long_string = long_string.replace('a', '*')
+print(long_string)
+
+#-------------------------------------------------------  
+# 8) Solution
+ll = [1, 2, 3, 4, 5]
+
+ll.reverse()
+print(ll)
+#ll.pop(1) 
+# or better
+ll.pop(ll.index(4))
+print(ll)
+ll.append(1.5)
+print(ll)
+ll.sort()
+print(ll)
+
+#%% #-------------------------------------------------------  
+# 9) Solution
+number = "32,054.23"
+number_no_comma = number.replace(',', '')
+number_float = float(number_no_comma)
+print(number_float)
+
+#or
+print(float(number.replace(',', '')))
+
+#-------------------------------------------------------  
+# 10) Solution
+firstname_lastname = 'john_doe'
+firstname, lastname = firstname_lastname.split('_')
+Firstname = firstname.capitalize()
+Lastname = lastname.capitalize()
+print(Firstname, Lastname)
+#-------------------------------------------------------  
+# 11-12) Solution
+l = [0, 1, 2, 4, 5]
+index = l.index(4)
+l.insert(index, 3)
+print(l)
+
+#-------------------------------------------------------  
+# 13) Solution
+s = 'www.example.com'
+s = s.lstrip('w.')
+s = s.rstrip('.c')
+
+# or in a single line
[…]

### 2017-02-13 Documents/bootcamp_practice_pyfund2.tex
add practice_pyfund2

\documentclass[11pt]{exam}

\input{../LaTeX/preamble.tex}

%\printanswers

% document starts here
\begin{document}
%\parskip=\bigskipamount
\parindent=0.0in
\thispagestyle{empty}
%\input{../LaTeX/header.tex}

\bigskip\bigskip
\centerline{\Large \bf Data Bootcamp:  Python Fundamentals 1 Practice}
\centerline{Revised: \today}

\medskip

\vspace{2cm}

\begin{questions}
\item Construct a dictionary whose keys are the integers $1$, $2$ and $3$ and whose values are the same numbers as words: one, two, three. How would you get the word associated with the key 2?

\item What does the built-in function \texttt{zip()} do? Start with the lists
\begin{verbatim}
l1 = [1, 2, 3]
l2 = ['one', 'two', 'three']
\end{verbatim} 
\begin{itemize}
\item Construct the list of tuples \texttt{[(1, 'one'), (2, 'two'), (3, 'three')]}.
\item Construct a dictionary whose keys are the integers $1$, $2$ and $3$ and whose values are the same numbers as words: one, two, three.  
\end{itemize}

\item Take the variables \texttt{name1} and \texttt{name2}, both of them strings. Write a program using \texttt{if ... else} that prints the name that comes first in alphabetical order. Test your program with 
\begin{verbatim}
name1 = 'Dave'
name2 = 'Glenn'
\end{verbatim}
Could you write a function for this task?

\item Take the list \texttt{stuff = ['cat', 3.7, 5, 'dog']}. 
\begin{itemize}
\item Write a program that tells us the type of each elements of \texttt{stuff} (value and type)
\item Write a program that prints only the elements of \texttt{stuff} that are strings. 
\end{itemize}

\item Write a program that given two integer values \texttt{a} and \texttt{b} returns \texttt{True} if either one is $6$, or if their sum or difference is $6$. \emph{Hint:} you might want to use the built-in function \texttt{abs()}. Test your program with
\begin{itemize}
\item \texttt{a=6}, \texttt{b=4} (should get \texttt{True})
\item \texttt{a=4}, \texttt{b=5} (should get \texttt{False})
\item \texttt{a=1}, \texttt{b=5} (should get \texttt{True})
\end{itemize}
Could you write a function for this task?

\item Write a program that given two integers \texttt{a} and \texttt{b} returns their sum. However, sums in the range $[10, 19]$ are forbidden, so in that case just return $20$. Test your program with
\begin{itemize}
\item \texttt{a=3}, \texttt{b=4} (should get $7$)
\item \texttt{a=9}, \texttt{b=4} (should get $20$)
\item \texttt{a=10}, \texttt{b=11} (should get $21$)
\end{itemize}
Could you write a function for this task?

\item Take the list of bond yields \texttt{y = [.01, .02, .03]} for maturities of one, two and three years. Write a program that multiplies all elements with 100, i.e. returns the list 
\begin{verbatim}
y_perc = [1.0, 2.0, 3.0]
\end{verbatim}
Can you do it with list comprehension? And with a function?

\item Using only core \texttt{Python} functionality define a list that contains 
\begin{itemize}
\item all integers from 0 to \texttt{n} (test it with the example: \texttt{n=5})
\item all integers from \texttt{n1} to \texttt{n2} (test it with the example: \texttt{n1=4} and \texttt{n2=8}) 
\end{itemize}
Could you define a function that can do both? (\emph{Hint:} use default values)

\begin{center}
\noindent\rule{10cm}{0.4pt}
\end{center}

\item Suppose that you have two strings
\begin{verbatim}
s1 = "abc def ghi"
s2 = "def ghi abc"
\end{verbatim}
\begin{itemize}
\item How would you check if the two strings contain the same characters? (irrespective of their order)
\item How would you check if the two strings contain the same words?
\end{itemize}

\item Take the list \texttt{x = [1, 4, 5, 6, 4, 2, 7, 12, 4, 23, 4]}. Using only loops and/or conditionals create a list with all the indices \texttt{i} for which 
\texttt{x[i] == 4}.

\end{questions}
%\input{../LaTeX/footer.tex}

\end{document}

### 2017-02-13 Documents/bootcamp_practice_pyfund1.tex

\documentclass[11pt]{exam}

\input{../LaTeX/preamble.tex}

%\printanswers

% document starts here
\begin{document}
%\parskip=\bigskipamount
\parindent=0.0in
\thispagestyle{empty}
%\input{../LaTeX/header.tex}

\bigskip\bigskip
\centerline{\Large \bf Data Bootcamp:  Python Fundamentals 1 Practice}
\centerline{Revised: \today}

\medskip
%{\it Answer each of the questions below.
%Include any code you write.
%What you hand in can be code or handwritten or something else,
%but it must be readable and professional.
%Hardcopy only.}
\vspace{2cm}

\begin{questions}
\item Fix this code:
\begin{verbatim}
bad_string = 'Sarah's code'
\end{verbatim}

\item How would you convert the integer i = 1234 to the list 
\begin{verbatim}
l = ['1', '2', '3', '4']
\end{verbatim}

\item Suppose \textbf{year} is a string containing the year of a particular piece of data; for example, 
\begin{verbatim}
year = '2016'
\end{verbatim}
How would we construct a \emph{string} for the following year?

\item Suppose we have two variables, $x$ and $y$. How would you switch their values, so that $x$ takes on $y$'s value and $y$ takes on $x$'s?

\item Set 
\begin{verbatim}
name = 'Jones'
\end{verbatim}
Use (a) tab completion to find a method that coverts \textbf{name} to upper case (capital) letters and (b) the Object inspector to find out how to use that method.

\item Set 
\begin{verbatim}
name = 'Ulysses'
\end{verbatim}
Use (a) tab completion to find a method that counts the number of appearances of the letter $s$ and (b) the Object inspector to find out how to use that method.

\item Set
\begin{verbatim}
long_string = 'salamandroid'
\end{verbatim}
Find a method to replace the $a$'s with asterisks.

\item Create the list 
\begin{verbatim}
list = [1, 2, 3, 4, 5]
\end{verbatim}
and using list methods
\begin{itemize}
\item reverse the elements of $l$ and print it
\item remove the number $4$ from $l$ and print it 
\item append the float $1.5$ to $l$ and print it
\item sort the elements of $l$ and print it
\end{itemize}

\begin{center}
\noindent\rule{10cm}{0.4pt}
\end{center}

\pagebreak

\item You are given the number (as a string) in the following form
\begin{verbatim}
number = "32,054.23"
\end{verbatim}
How would you convert this into a valid float? You should get $32054.23$.

\item You are given a name of the form 
\begin{verbatim}
firstname_lastname = 'john_doe'
\end{verbatim}
Save Firstname and Lastname variables with capitalized values using string methods.

\item You are given a list of the form: $l = [0, 1, 2, 4, 5]$. Use methods for lists to produce a corrected list which contains the number $3$ between $2$ and $4$:

\begin{verbatim}
l = [0, 1, 2, 3, 4, 5]
\end{verbatim}

\item You are given a list of the form: $l = [\dots, 1, 2, 4, 5, \dots]$ (with an ``unkown'' number of first and last elements). Use methods for lists to produce a corrected list which contains the number $3$ between $2$ and $4$:

\begin{verbatim}
l = [..., 1, 2, 3, 4, 5, ...]
\end{verbatim}

\item You are given strings of web domains of the form: $s = $'www.example.com'. You want to strip the \textbf{'www.'} and the \textbf{'.com'}. Use string methods to achieve this.

\item Write a Python program to get the part of the string 
\begin{verbatim}
link = 'https://play.spotify.com/collection/albums'
\end{verbatim}
before the last '/' character. You should get \begin{verbatim}
'https://play.spotify.com/collection'
\end{verbatim}

\item \textbf{Hard!} Write a program to swap comma and dot in a string. In particular turn the string
\begin{verbatim}
dot_comma = "32.054,23"
\end{verbatim}
into
\begin{verbatim}
comma_dot = "32,054.23"
\end{verbatim}
\emph{Hint:} look up the string methods \textbf{maketrans} and \textbf{translate}.
\end{questions}

%\input{../LaTeX/footer.tex}

\end{document}

### 2017-02-14 Code/Python/py_fundamentals2.py
add pyfund2

@@ -1,0 +1,354 @@
+"""
+Python Fundamentals 2
+
+@author: Balint Szoke
+@date:   2/11/2017
+"""
+
+"""---------------------------------------------------
+REVIEW
+---------------------------------------------------"""
+
+# Assignment
+x = 3.14                
+
+# Strings
+s = 'this is a string'      
+type(s)
+len(s)
+
+# Lists
+l = [1, 'help', 12.14]
+print('This is a', type(l), 'containing', len(l), 'items')
+
+#change types with  str(), int(), float()
+
+#Methods
+'s is {t} with {c} chars'.format(t=type(s), c=len(s))
+l.append(x)
+print(l)
+
+# Tab completion!
+
+#%%
+"""---------------------------------------------------
+OTHER NATIVE PYTHON DATA TYPES
+---------------------------------------------------"""
+
+#====================
+# Dictionary
+#====================
+
+dict1 = {'first': 12, 'second': 20, 3: 'first'}
+print(dict1)
+type(dict1)
+
+# Unordered, access values through keys 
+dict1['first']
+dict1[3]
+# dict1[0]                    # indexing doesn't work
+
+#Key must be unique (only keeps last one)
+dict2 = {'first': 12, 'first': [4, 1]}
+print(dict2)
+
+# Key must be inmutable! What's the problem?
+#dict3 = {[1, 2]: 4}
+
+# Methods
+dict1.keys()
+dict1.values()
+
+list(dict1)
+list(dict1.values())
+
+#==========================
+# Boolean (comparisons)
+#==========================
+
+# Yes/no questions
+4 < 5           # interpreted as: is 5 greater than 4?       
+x > 5           # can involve variables
+type(x > 5)
+z = x > 5       # True/False value can be assigned
+
+# Basic comparison operators
+x == 3          # equal to?
+5 >= 5          # greater than or equal to?
+x != 3          # not equal to? 
+
+# True == 1, False == 0
+int(z)
+
+# can reverse comparisons with "not"
+not 3 > 5
+
+# Use it the usual way
+x, y = 4*2, 2**3
+"x={x}, y={y}, so x>y is {s}".format(x=x, y=y, s=x>y)
+
+type('Sarah') == str      # can involve "type checking"
+len('Sarah') >= 3
+
+# Tricky one
+name1 = 'Chase'
+name2 = 'Spencer'
+
+name1 > name2
+name1 < name2
+# what's going on? try
+'a' < 'b'
+
[…]

### 2017-03-21 Documents/bootcamp_project.tex
post spring break cleanup

@@
 you get 5 points if you do them, none if you don't.
-We start with individual work.  Partway along, we encourage you to form groups
-of two or three, but if you'd prefer to do this on your own,
+We start with individual work.  Partway along, we encourage you to form \textbf{groups
+of two or three}, but if you'd prefer to do this on your own,
 that's ok, too.
@@
 Three Project Ideas         & Paper (hand-written)  & Individual  & 0  \\
-Three Revised Project Ideas & Paper (professional)  & Individual  & 5  \\
+%Three Revised Project Ideas & Paper (professional)  & Individual  & 5  \\
 Project Proposal            & Paper (professional)  & Group       & 5  \\
 Data Report                 & Paper (professional)  & Group       & 5  \\
-Final Project               & Jupyter notebook      & Group       & 85 \\
+Final Project               & Jupyter notebook      & Group       & 90 \\
 \bottomrule
@@
 
-\item {\bf Three revised project ideas.}
-After giving this more thought, write down three project ideas in (a little) more detail.
-{\bf Include likely data sources.}
+%\item {\bf Three revised project ideas.}
+%After giving this more thought, write down three project ideas in (a little) more detail. {\bf Include likely data sources.}
 %Ask questions; we have a lot of experience with this, especially data.
-All together this should be roughly one paragraph per idea and one page overall.
-Like all work in this course, it should be clean and professional.
+%All together this should be roughly one paragraph per idea and one page overall. Like all work in this course, it should be clean and professional.
 %We will keep the copy you hand in to use in class, so keep a separate copy for yourself.
 
-{\bf We will not give you written feedback} on your ideas,
-but {\bf we would be happy to talk in person}, either before class or another time.
-Our experience is that exchanges like this work much better in person,
-where we can bounce ideas around in ways that are hard to replicate in writing.
+%{\bf We will not give you written feedback} on your ideas, but {\bf we would be happy to talk in person}, either before class or another time.
+Our experience is that exchanges like this work much better in person, where we can bounce ideas around in ways that are hard to replicate in writing.
 
@@
 
-{\bf Did we mention data?}
+%{\bf Did we mention data?}
 
@@
 \item {\bf Final project.}
-You should submit your {\bf Jupyter notebook\/} to \href{mailto:nyu.databootcamp@gmail.com}{nyu.databootcamp@gmail.com}
-by the due date listed on the course website.
-The subject line should be:  ``bootcamp project ug'' or ``bootcamp project mba''
-depending on the section you are in.
+You should submit your {\bf Jupyter notebook\/} to %\href{mailto:nyu.databootcamp@gmail.com}{nyu.databootcamp@gmail.com}
+NYU Classes by the due date listed on the course website.
+%The subject line should be:  ``bootcamp project ug'' or ``bootcamp project mba'' depending on the section you are in.
 The file name should be your last names separated by dashes and a short title ---

### 2017-08-17 Documents/bootcamp_syllabus.tex
update links to website
Updating Syllabus

@@
-\documentclass[11pt]{article}
+%\documentclass[11pt]{article}
 
-\input{../LaTeX/preamble.tex}
+%%%%%%%%%%%%%%%%%%%%%% Stock Preamble %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-% document starts here
+\input{../LaTeX/undergrad_preamble.tex}
+
+%%%%%%%%%%%%%%%%%%%%%%Headers and Footers%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\pagestyle{headandfoot}
+\runningheadrule
+\firstpageheadrule
+\firstpageheader{\includegraphics[width=0.25\textwidth]{../Figures/stern_black1.pdf}}{}{Data Bootcamp}
+\runningheader{Data Bootcamp}{}{Syllabus: ECON-UB.0011.02}
+\runningfooter{}{}{}
+
 \begin{document}
-\parskip=\bigskipamount
-\parindent=0.0in
-\thispagestyle{empty}
-\input{../LaTeX/header.tex}
+\centerline{\Large\bf Syllabus:  Data Bootcamp}
+\vspace{3mm}
+\centerline{\large\bf ECON-UB.0232 $|$ Fall 2017}
+\vspace{3mm}
+\centerline{\bf Revised:  \today}
 
-\bigskip\bigskip
-\centerline{\Large \bf Data Bootcamp:  Syllabus}
-\centerline{Revised: \today}
-
-\section*{Overview}
+\bigskip
+%\vspace{-.25cm}
 
@@
 data, and enough about computer programming to work with it effectively.
-Applications include some or all of: leading economic indicators; emerging market country indicators;
-bond and equity returns; stock options; education and income; income by zip code; long tail sales data; innovation diffusion curves; and many others.
+Applications include some or all of: leading economic indicators; emerging market country indicators; bond and equity returns; stock options; education and income; income by zip code; long tail sales data; innovation diffusion curves; and many others.
+
 We will use Python, a popular high-level computer language that's widely used in finance, consulting,
-technology, and other parts of the business world.
-``High-level'' means it's less painful than most (the hard work is done by the language),
-but it's a serious language with extensive capabilities.
+technology, and other parts of the business world. ``High-level'' means it's less painful than most (the hard work is done by the language), but it's a serious language with extensive capabilities.
+
 ``Data analysis'' means primarily graphical descriptions that summarize data
 in ways that are helpful and informative.
-``Bootcamp'' is a reminder that expertise takes work. Don't worry, it's worth it.
-{\bf You will be more valuable to current and future employers.\/}
-And you will be able to do more things more efficiently than
-friends who rely on Excel.
+``Bootcamp'' is a reminder that expertise takes work.
+Don't worry, it's worth it.
+{\bf You will be more valuable to current and future employers.\/} And you will be able to do more things more efficiently than friends who rely on Excel.
 
-If you're not convinced --- or even if you are ---
-we have a more elaborate sales pitch on the
-\href{http://databootcamp.nyuecon.com/}{course website}.
+If you're not convinced|or even if you are|we have a more elaborate sales pitch on the
+\href{https://nyu.data-bootcamp.com/}{course website}.
 
@@
 
-\section*{Requirements}
+\subsubsection*{About the Instructor}
+\href{http://www.waugheconomics.com}{Professor Michael Waugh} \\
+Email: mwaugh@stern.nyu.edu\\
+Office: KMC 7-74\\
+Phone: 212-998-0288\\
+Office hours: TBA, Monday and Wednesday.
+
+\subsubsection*{Where and When}
+Monday and Wednesday \\
+%Section \#2: TISCH UC24, 3:30PM - 4:45PM
+
+\subsection*{Requirements}
 
@@
 \begin{center}
-\url{http://databootcamp.nyuecon.com/}
+\url{http://nyudatabootcamp.github.io/website/}
 \end{center}

### 2017-08-22 Documents/bootcamp_syllabus.tex
Updated Syllabus

@@
 
-There are two sections of this course,
-one for undergrads (ECON-UB.0232) and one for MBA students (ECON-GB.2313).
-The content is the same, but the schedules are different.
-
 \subsubsection*{About the Instructor}
 \href{http://www.waugheconomics.com}{Professor Michael Waugh} \\
-Email: mwaugh@stern.nyu.edu\\
+Email: \href{mailto:mailto:mwaugh@stern.nyu.edu}{mwaugh@stern.nyu.edu}\\
 Office: KMC 7-74\\
@@
 \subsubsection*{Where and When}
-Monday and Wednesday \\
-%Section \#2: TISCH UC24, 3:30PM - 4:45PM
+Meeting times: Monday and Wednesday 330-445pm\\
 
-\subsection*{Requirements}
+Meeting place: KMC 5-140
+
+\section*{Requirements}
 
@@
 
-This course has a strong {\bf support system\/} to help you when you run into problems ---
-and anyone who codes runs into problems.
-Each section has two teachers and a teaching assistant, all of them happy to answer your questions.
-You can also post questions on our discussion group (see below).
+This course has a strong {\bf support system\/} to help you when you run into problems|and anyone who codes runs into problems.
+We have a myself and a teaching fellow to help.
+Below is the contact info for our teaching fellow this semester.
+
+\textbf{Teaching Fellows}\\
+\\
+Felipe Alves 
+Email: \href{mailto:mailto:falves@stern.nyu.edu}{falves@stern.nyu.edu}\\
+Office hours: TBA\\
+
+Guess what\ldots you also have classmates that can help!!!
+You can post questions (and maybe answer your classmates questions) on our discussion group (see below).
+Felipe and I will also monitor the discussion group.
 
@@
 
-Eveything you need, including this document, is posted on
+Everything you need, including this document, is posted on
 the {\bf course website\/}:
@@
 \begin{center}
-\url{http://nyudatabootcamp.github.io/website/}
+\url{https://nyu.data-bootcamp.com/undergrad_outline/}
 \end{center}
@@
 \begin{center}
-UG:   \url{https://groups.google.com/forum/#!forum/nyu_data_bootcamp_ug}  \\
-MBA:  \url{https://groups.google.com/forum/#!forum/nyu_data_bootcamp_mba}
+\url{https://groups.google.com/d/forum/databootcamp_fall2017_undergrad} 
 \end{center}
 \vspace{-0.1in}
-%
 You can access the same links from the course website.  Follow the instructions to join under whatever email address you plan to use.
@@
 After each topic, we recommend you:
-% write everything you remember without looking
-%at your notes or the book.  Note any gaps in your knowledge.
-%Then read the book, work through the exercises, and fill in the gaps.
-%Ask
-%
-%\begin{comment}
 \begin{itemize}
 \item {\it Write:\/}  Shortly after class, write down everything you remember
-without looking at your notes or the book. Note things you don't understand --- gaps, we call them.
+without looking at your notes or the book. Note things you don't understand|gaps, we call them.
+
 \item {\it Review:\/} Read the relevant section of the book.  Fill in the gaps. Ask for help with anything you still don't understand.
-%\item {\bf Review:\/} Later on, go through what you wrote down earlier and  fill in the gaps
-%by using the book.
 \end{itemize}
-%\end{comment}
-%
 
@@
 You can find answers to common questions on the course website.
-You can also post questions on the discussion group;
-see the link above and on the course website.
-For others, email us (\href{mailto:nyu.databootcamp@gmail.com}{nyu.databootcamp@gmail.com}),
-the co-teacher, or the teaching fellow; their contact information is on the course website.
+You can also post questions on the discussion group; see the link above and on the course website.
+For others, email me or the teaching fellow.
 
@@
 You should instead download them to your own computer and open them there.
-To download them,
-click on the Raw button above the document.
+To download them, click on the Raw button above the document.
 To view them, use Adobe Acrobat Reader or the equivalent (FoxIt, Sumatra, etc).
@@
 
-\input{../LaTeX/footer.tex}
+%\input{../LaTeX/footer.tex}
 

### 2017-08-28 Documents/bootcamp_syllabus.tex
Updated Syllabus
Dates added to Syllabus

@@
 \subsubsection*{Where and When}
-Meeting times: Monday and Wednesday 330-445pm\\
+Meeting times: Monday and Wednesday 330-445pm
 
 Meeting place: KMC 5-140
+
+\subsection*{Important Dates}
+
+Midterm Exam: \textbf{November 8, 2017}. Quick info: 75 minutes, in class, open book, open internet if the wireless is up, bring one page of notes. \\
+
+\href{https://github.com/NYUDataBootcamp/Materials/blob/master/Documents/bootcamp_project.pdf}{Final Project} Due Date: End of day \textbf{December 21, 2017.}
 
@@
 \\
-Felipe Alves 
+Felipe Alves \\
 Email: \href{mailto:mailto:falves@stern.nyu.edu}{falves@stern.nyu.edu}\\

### 2017-09-04 Documents/bootcamp_3ideas.tex
Outline and ideas change

--- 2017-08-22 Documents/bootcamp_syllabus.tex
@@
-%\documentclass[11pt]{article}
-
 %%%%%%%%%%%%%%%%%%%%%% Stock Preamble %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \firstpageheadrule
-\firstpageheader{\includegraphics[width=0.25\textwidth]{../Figures/stern_black1.pdf}}{}{Data Bootcamp}
-\runningheader{Data Bootcamp}{}{Syllabus: ECON-UB.0011.02}
+\firstpageheader{\includegraphics[width=0.25\textwidth]{../Figures/stern_black1.pdf}}{}{Data Bootcamp: Three Project Ideas}
+\runningheader{}{}{}
 \runningfooter{}{}{}
@@
 \begin{document}
-\centerline{\Large\bf Syllabus:  Data Bootcamp}
-\vspace{3mm}
-\centerline{\large\bf ECON-UB.0232 $|$ Fall 2017}
-\vspace{3mm}
-\centerline{\bf Revised:  \today}
+\bigskip
+\centerline{\Large \bf Data Bootcamp: Three Project Ideas}
+\medskip
+\centerline{Revised: \today}
 
 \bigskip
-%\vspace{-.25cm}
-
-Data Bootcamp is about nuts and bolts data analysis. You will learn about economic, financial, and business
-data, and enough about computer programming to work with it effectively.
-Applications include some or all of: leading economic indicators; emerging market country indicators; bond and equity returns; stock options; education and income; income by zip code; long tail sales data; innovation diffusion curves; and many others.
-
-We will use Python, a popular high-level computer language that's widely used in finance, consulting,
-technology, and other parts of the business world. ``High-level'' means it's less painful than most (the hard work is done by the language), but it's a serious language with extensive capabilities.
-
-``Data analysis'' means primarily graphical descriptions that summarize data
-in ways that are helpful and informative.
-``Bootcamp'' is a reminder that expertise takes work.
-Don't worry, it's worth it.
-{\bf You will be more valuable to current and future employers.\/} And you will be able to do more things more efficiently than friends who rely on Excel.
-
-If you're not convinced|or even if you are|we have a more elaborate sales pitch on the
-\href{https://nyu.data-bootcamp.com/}{course website}.
-
-\subsubsection*{About the Instructor}
-\href{http://www.waugheconomics.com}{Professor Michael Waugh} \\
-Email: \href{mailto:mailto:mwaugh@stern.nyu.edu}{mwaugh@stern.nyu.edu}\\
-Office: KMC 7-74\\
-Phone: 212-998-0288\\
-Office hours: TBA, Monday and Wednesday.
-
-\subsubsection*{Where and When}
-Meeting times: Monday and Wednesday 330-445pm\\
-
-Meeting place: KMC 5-140
-
-\section*{Requirements}
-
-There are no prerequisites.
-{\bf We welcome students with no prior programming experience\/}
-and have designed the course with them in mind.
-What you need is the {\bf courage\/} to take on a challenge
-and the {\bf patience\/} to fix computer programs that don't work.
-That's a regular occurrence, even for experts.
-
-Our one requirement is that {\bf you must bring a laptop computer to class\/}.
-It should be your own computer, or at least one you can install new programs on.
-We will use it constantly in class, writing and correcting short programs.
-
-\section*{Getting help}
-
-This course has a strong {\bf support system\/} to help you when you run into problems|and anyone who codes runs into problems.
-We have a myself and a teaching fellow to help.
-Below is the contact info for our teaching fellow this semester.
-
-\textbf{Teaching Fellows}\\
-\\
-Felipe Alves 
-Email: \href{mailto:mailto:falves@stern.nyu.edu}{falves@stern.nyu.edu}\\
-Office hours: TBA\\
-
-Guess what\ldots you also have classmates that can help!!!
-You can post questions (and maybe answer your classmates questions) on our discussion group (see below).
-Felipe and I will also monitor the discussion group.
-
-The bottom line:  {\bf If you're stuck, ask for help\/}.
-Really.  Don't be a hero, ask for help.
-
-\section*{Course website and discussion groups}
-
-Everything you need, including this document, is posted on
-the {\bf course website\/}:
-%
-\vspace{-0.15in}
-\begin{center}
-\url{https://nyu.data-bootcamp.com/undergrad_outline/}
-\end{center}
-\vspace{-0.15in}
-%
-The {\bf book\/} has its own site,
-\vspace{-0.15in}
-\begin{center}
-\url{https://www.gitbook.com/book/nyudatabootcamp/data-bootcamp/details}
-\end{center}
-\vspace{-0.15in}
-%
-There's a link to it on the course site.
-We will not use NYU Classes.
-
-We have set up {\bf announcement and discussion groups\/} (Google groups)
-to make announcements and post questions. We will use this to post all assignments and
-answer keys.
-If you have coding or other questions, we encourage you to post them there.
-If you know the answer to someone else's question, we {\bf strongly } encourage you to post that, too.
-The links are
-\vspace{-0.1in}
-\begin{center}
-\url{https://groups.google.com/d/forum/databootcamp_fall2017_undergrad} 
-\end{center}
-\vspace{-0.1in}
-You can access the same links from the course website.  Follow the instructions to join under whatever email address you plan to use.
-
-\section*{Deliverables and grades}
-
-The course divides naturally into two parts.
-The first part is an introduction to those aspects of the Python programming language
-useful for data analysis.
-We cover this material with as many applications to real data as we can think of.
-It ends with an exam.
-The second part covers advanced topics and ends with a project of your own.
-The goal is for you to have a piece of work you can show potential employers to
-illustrate your quantitative skill set.
-Both parts include a number of graded deliverables.
-The idea is to {\bf do some work all the time rather than lots of work once in a while.}
-We don't believe the latter will work.
-
-Graded work includes:
-%
-\begin{itemize}
-
-\item {\bf Code Practice.\/}
-There are three such assignments in the first month.
-We encourage you do to all of them --- they're good practice ---
-but your grade will be based on the best two. We find that people who finish these assignments
-tend to keep up with the material better and these are easy points to get in terms of grades.
-We will also distribute Optional Code Practice ``assignments,''
-but they will not be collected or graded.
-They are, however, a good way to develop your coding skills.
-
-{\it These assignments have questions that range from easy to moderately difficult,
-the latter marked {\it challenging\/}.
-They're all good practice, but if you're new to programming you
-might want to skip the challenging ones.
-If you get 70-80 percent of them, you're on the right track. \/}
-
-\item {\bf Examination.\/}
-The exam will cover material from the first half of the course.
-It takes 75 minutes and will be held in class.
-It will involve coding.
-{\bf Bring your computer.\/}
-We suggest you also {\bf bring one page of notes\/}.
-If the internet is working you will be able to look things up on there.
-If not, your notes will save you.
-It's also a good study tool:  When you decide what to include,
-you'll be organizing your thoughts about what you've learned.
-
-\item {\bf Project.\/}
-We work our way up to the project one step at a time, starting with idea generation and ending
-with a {\bf professional piece of data collection and analysis\/}
-that you can share with potential employers.
-The structure of the project is laid out in a separate document. We have found that the quality
-of final project had a surprisingly low correlation to previous programming experience. A little thought and
-effort go a long way in creating an interesting project.
-
-\end{itemize}
-
-{\bf Due dates} are posted on the course website.
-Assignments, whether code practice or components of the project,
-are due at the start of class on the specified dates.
-
-{\bf Dates are not negotiable.
-Anything handed in late will get a grade of zero.\/}
-
-{\bf All your work should be clean and professional.}  Your grade depends on it.
-
-{\bf Final grades\/} will be computed from
-\begin{center}
-\begin{tabular}{ll}
-Code Practice (best two of three) & 20\% \\
-Exam        & 30\% \\
-Project     & 50\% \\
-\end{tabular}
-\end{center}
-
-Final grades are not subject to any fixed distribution or curve.
-The number of A grades, for example,
-will depend only on your performance in the course.
-If you make a good-faith effort,
-we expect it to be hard to get less than a B.
-We are the sole judges of what constitutes good-faith effort.
-
-\section*{Recommended work habits}
-
-Python is not something you can learn from reading a book and attending lectures.
-You need to {\bf write programs\/} ---
-the more the better --- to understand how they work.
-Think about how you'd learn to play basketball or soccer;
-reading and listening to lectures aren't enough, you need to do it.
-We'll do a lot of programming in class, but it's {essential\/} that you
-follow up outside of class.
-Here's how.
-
-{\bf Write \& Review.\/}
-After each topic, we recommend you:
-\begin{itemize}
-\item {\it Write:\/}  Shortly after class, write down everything you remember
-without looking at your notes or the book. Note things you don't understand|gaps, we call them.
-
-\item {\it Review:\/} Read the relevant section of the book.  Fill in the gaps. Ask for help with anything you still don't understand.
-\end{itemize}
-
-{\bf Practice.\/}
-For the first half of the term, each topic has an assignment that covers the same material.
-We suggest you do them, even the ones that aren't graded.
-
-We also recommend you {\bf practice coding\/} whenever you have the chance.
-Start small. Write short programs to do anything that crosses your mind.
-Use Python to do things you would ordinarily do in Excel.
-Try doing assignments from other courses in Python.
-At first this will be more work than doing it by hand or in Excel,
-but once you have some experience it will typically be easier in Python.
-Even if that's not the case, the practice will expand your skill set.
-
-\section*{Pacing}
-
-The course is designed to be cover material at whatever pace the class is capable of.
-The topics should take roughly one week each, but we can scale that up or down as needed.
-If you're an expert, don't worry, we'll cover a lot of material either way.
-
-\section*{Other questions}
-
-You can find answers to common questions on the course website.
-You can also post questions on the discussion group; see the link above and on the course website.
-For others, email me or the teaching fellow.
-
-\section*{Viewing and printing pdf files}
-
-This document and most others in the course are pdf's that we hand out in class and post on GitHub.
-If you view them online, the links won't work; that's an unfortunate feature of GitHub's pdf viewer.
-You should instead download them to your own computer and open them there.
-To download them, click on the Raw button above the document.
-To view them, use Adobe Acrobat Reader or the equivalent (FoxIt, Sumatra, etc).
-The links should then work.
-
-For Mac OS users, Preview has this problem and others; for example,
-links don't work and some fonts don't display or print.
-The solution is to install Adobe Acrobat Reader or the equivalent
-and set it up as your default for pdf files.
-
-\section*{Policies}
-
-Ethics, disabilities, and many other things are governed by NYU
-and Stern policies.
-If you have questions about them, please ask.
-
-On graded work:
-You may discuss assignments with anyone (in fact, we encourage it),
-but anything you submit, including your code, should be your own.
-Exams should be entirely your own work.
-
-On disabilities:
-If you have a qualified disability that requires academic accommodation,
-please contact the Moses Center for Students with Disabilities
-(\href{http://www.nyu.edu/life/safety-health-wellness/students-with-disabilities.html}{CSD},
-212-998-4980) and ask them to
-send us a letter verifying your registration and outlining the accommodation they recommend.
-If you need to take an exam at the CSD,
-you must submit a completed Exam Accommodations Form to them
-at least one week prior to the scheduled exam time to be assured accommodation.
+{\it Write down three project ideas, a sentence or two each. We'll use them for class discussion. 
+Save for later, they're a head start on coming up with a project idea.}
 

### 2017-09-04 Documents/bootcamp_topic_intro.tex
Outline and ideas change

@@
-\documentclass[11pt]{article}
+%%%%%%%%%%%%%%%%%%%%%% Stock Preamble %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\input{../LaTeX/preamble.tex}
+\input{../LaTeX/undergrad_preamble.tex}
 
-% document starts here
+%%%%%%%%%%%%%%%%%%%%%%Headers and Footers%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\pagestyle{headandfoot}
+\runningheadrule
+\firstpageheadrule
+\firstpageheader{\includegraphics[width=0.25\textwidth]{../Figures/stern_black1.pdf}}{}{Data Bootcamp: Three Project Ideas}
+\runningheader{}{}{}
+\runningfooter{}{}{}
+
 \begin{document}
-\parskip=\bigskipamount
-\parindent=0.0in
-\thispagestyle{empty}
-\input{../LaTeX/header.tex}
-
-\bigskip\bigskip
+\bigskip
 \centerline{\Large \bf Topic Outline:  Data + Python}
+\medskip
 \centerline{Revised: \today}
@@
 \item  Today's handouts:  this outline, three ideas (two copies), book chapters, red/green stickers
-\item  All posted on {\it Topic list \& links\/} page of website (except the stickers).
+\item  All posted on website (except the stickers).
 \end{itemize}
@@
 \item Google ``nyu data bootcamp''
-\item Website (thanks, Spencer):  \url{http://databootcamp.nyuecon.com/}  (bookmark me!)
-\item Book
-\item Topic list \& links
-\item Discussion group
-\item Data page
+\item Website, topic list \& links  (thanks, Spencer):\\ \url{https://nyu.data-bootcamp.com/undergrad_outline/}  (bookmark me!)
+\item Book: \\ \url{https://www.gitbook.com/book/nyudatabootcamp/data-bootcamp/details}
+\item Discussion group: \\ \url{https://groups.google.com/d/forum/databootcamp_fall2017_undergrad}
+\item Data page: \\
+\url{https://nyu.data-bootcamp.com/data/}
 \item GitHub repository:  \url{https://github.com/NYUDataBootcamp/Materials}
@@
 \item Have fun
+\end{itemize}
+\end{itemize}
+
+\section*{Setting up your Computer}
+\begin{itemize}
+\item Create \verb|Data_Bootcamp| directory/folder on your computer. This is a place for you to save stuff to, work from, etc.  
+\item My style: To keep things simple I do the following
+\begin{itemize}
+\item Find your main hard drive, on PCs typically the ``C'' drive
+\item In the C drive, create a folder called \verb|Data_Bootcamp|
+\item Now if you every have to call this file you know it is \verb|c:\Data_Bootcamp|
+\end{itemize}
+\end{itemize}
+
+\section*{\href{https://github.com}{GitHub}}
+\begin{itemize}
+\item What I will use it for\ldots
+\begin{itemize}
+\item Source of ALL course materials
+\item Place for you to grab materials on the fly. Save files by cut and paste, clever save as, or "Raw" (ask about this)
+\end{itemize}
+\item You need to create an account and email me your username
+\item What you will use it for\ldots
+\begin{itemize}
+\item Post your homework and projects; I will ``pull'' them from there.
+\item Long run: Think of this like an artists portfolio. Here you can post your code and projects and show potential employers, family, friends what you have done.
 \end{itemize}
@@
 \item Environments?  (Analogy:  Word is an environment for creating Word docs.)
-%(environment is to program as Word is to Word doc)
 \item Spyder:  classic coding environment with editor and output windows
@@
 \end{itemize}
-
 \end{itemize}
@@
 \item Put red sticker on your laptop
-\item Create \verb|Data_Bootcamp| directory/folder on your computer.
-{\bf Raise your hand if you're not sure what that means or how to do it.}
 \item From Launcher, launch Spyder (labelled ``spyder-app'')
@@
 
-\item Run test program in Jupyter
-\begin{itemize}
-\item Put red sticker on your laptop
-\item From Launcher, launch Jupyter (labelled ``ipython-notebook'')
-\item Navigate to \verb|Data_Bootcamp| directory
-\item Open a new IPython notebook (New, Python 3)
-\item Change name from {\tt Untitled} to \verb|bootcamp_test|
-\item Look around (toolbar, menubar, code cells)
-\item Enter test program in code cell
-\item Run program (Cell, Run All)
-\item Look for correct output (last line should be {\tt 3.5.x etc})
-\item Switch to green sticker if it works
-\end{itemize}
+% Not going to talk about Jupyter now...
+%\item Run test program in Jupyter
+%\begin{itemize}
+%\item Put red sticker on your laptop
+%\item From Launcher, launch Jupyter (labelled ``ipython-notebook'')
+%\item Navigate to \verb|Data_Bootcamp| directory
+%\item Open a new IPython notebook (New, Python 3)
+%\item Change name from {\tt Untitled} to \verb|bootcamp_test|
+%\item Look around (toolbar, menubar, code cells)
+%\item Enter test program in code cell
+%\item Run program (Cell, Run All)
+%\item Look for correct output (last line should be {\tt 3.5.x etc})
+%\item Switch to green sticker if it works
+%\end{itemize}
 
@@
 \end{itemize}
-
-\item GitHub summary
-\begin{itemize}
-\item Source of course materials
-\item Save files by cut and paste, clever save as, or "Raw" (ask about this)
-\end{itemize}
-
 \end{itemize}
@@
 MS Word  & Word document  \\
-MS Excel & Excel file     \\
+ & Excel file     \\
 iTunes & \\
@@
 Spyder   &                \\
-         & IPython notebook \\
 \bottomrule
@@
 
-\input{../LaTeX/footer.tex}
-
 \end{document}
-
-**Outline**
-
-* Why are we doing this?
-* Install Anaconda
-* Data
-
-**Skills**
-
-Why skills?
-
-* Businesses want people with skills (duh!)
-
-Why code?
-
-* One of the skills businesses value (not the only one)
-* Do things Excel can't do, and do them faster
-
-Why Python?
-
-* User-friendly
-* Broad range of applications
-
-**Overview**
-
-Where we're headed
-
-* Think of a **picture** you'd like to produce -- a "visualization"
-* And about what **data** you'll need
-* And the **coding skills** to get there
-* Examples:  [Gapminder](http://www.gapminder.org/world/) | [cancer screening](http://www.vox.com/2015/10/28/9631500/does-mammography-work) | [Uber in NYC](http://fivethirtyeight.com/features/uber-is-serving-new-yorks-outer-boroughs-more-than-taxis-are/) | [mortality](http://www.pnas.org/content/early/2015/10/29/1518393112.full.pdf) | [earthquake](https://jawbone.com/blog/napa-earthquake-effect-on-sleep/)
-
-http://graphics.wsj.com/infectious-diseases-and-vaccines/
-
-http://www.nytimes.com/interactive/2016/01/07/us/drug-overdose-deaths-in-the-us.html
-
-Philosophy
-
-* Target **coding novices**, no prior experience required or expected
-* **Jump right in** the deep end of the pool, figure it out as we go
-* Not a typical programming course:  cover only those aspects of Python relevant to data work
-
-Rules to live by
-
-* **Don't panic**.  The jargon and concepts will seem mysterious at first, but if you keep with it they'll start to make sense.
-* **One step at a time.**  We'll go as slowly as we need.  Speed is the enemy, it leads to mistakes.
-* **Doing is learning.**  We'll set you up to teach yourself.  If you're stuck, either **ask for help** or practice your **Google fu** and find the answer with Google.
-
-**Prelaunch checklist**
-
-Install Anaconda
-
-* Google "anaconda download"
-* Download installer for **Python 3.5**
-* Run installer
-
-Locate this file in a browser
-
-* Google "nyu data bootcamp" and follow links
-* Or:  type in url at the top
-
-Save today's code file in a handy place
-
-* Create directory/folder \verb|Data_Bootcamp|
-* Click on code link above, then Raw button
-* Save file in `Data_Bootcamp` directory
-
-Launch
-
-* Look for **Launcher** in your programs
-* Start it up (takes a minute)
-* Click on **Spyder** (another minute)
-
-\input{../LaTeX/footer.tex}
-
-\end{document}

### 2017-09-05 Documents/bootcamp_project.tex
Updated Project Guide

--- 2016-09-06 Documents/bootcamp_project.tex
@@
-\documentclass[11pt]{article}
+%%%%%%%%%%%%%%%%%%%%%% Stock Preamble %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\input{../LaTeX/preamble.tex}
+\input{../LaTeX/undergrad_preamble.tex}
 
-% document starts here
+%%%%%%%%%%%%%%%%%%%%%%Headers and Footers%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\pagestyle{headandfoot}
+\runningheadrule
+\firstpageheadrule
+\firstpageheader{\includegraphics[width=0.25\textwidth]{../Figures/stern_black1.pdf}}{}{Data Bootcamp: Project Guide}
+\runningheader{}{Data Bootcamp: Project Guide}{}
+\runningfooter{}{}{}
+
 \begin{document}
-\parskip=\bigskipamount
-\parindent=0.0in
-\thispagestyle{empty}
-\input{../LaTeX/header.tex}
 
@@
 
-One of our goals is for you to produce a piece of work you can use
-to demonstrate your data and programming skills to potential employers.
+One of our goals is for you to produce a piece of work you can use to demonstrate your data and programming skills to potential employers.
 That work will come in the form of a Jupyter notebook,
 a format that combines code, text, and graphics in one user-friendly document.
-We will add them to our GitHub repository so that
-you can use a link to show others what you've done.
-You will also be able to see what your classmates have done.
+The end product should be posted on your GitHub account in a repository so that
+you show others what you've done. You will also be able to see what your classmates have done.
 
@@
 We think that also makes them more interesting.
-They give you a chance to
-indulge your curiosity and show off your creativity.
+They give you a chance to indulge your curiosity and show off your creativity.
 
@@
 The intent is to make the project easier by breaking it down into a number
-of small, manageable sub-projects.
-The early steps are graded only on whether you do them:
+of small, manageable sub-projects. The early steps are graded only on whether you do them:
 you get 5 points if you do them, none if you don't.
-We start with individual work.  Partway along, we encourage you to form groups
-of two or three, but if you'd prefer to do this on your own,
-that's ok, too.
+We start with individual work.  Partway along, we encourage you to form \textbf{groups
+of two or three}, but if you'd prefer to do this on your own, that's ok, too.
 
@@
 \item {\bf Three revised project ideas.}
-After giving this more thought, write down three project ideas in (a little) more detail.
-{\bf Include likely data sources.}
-%Ask questions; we have a lot of experience with this, especially data.
-All together this should be roughly one paragraph per idea and one page overall.
-Like all work in this course, it should be clean and professional.
-%We will keep the copy you hand in to use in class, so keep a separate copy for yourself.
+After giving this more thought, write down three project ideas in (a little) more detail. {\bf Include likely data sources.}
+Ask questions; we have a lot of experience with this, especially data.
+All together this should be roughly one paragraph per idea and one page overall. Like all work in this course, it should be clean and professional.
+We will keep the copy you hand in to use in class, so keep a separate copy for yourself.
 
-{\bf We will not give you written feedback} on your ideas,
-but {\bf we would be happy to talk in person}, either before class or another time.
-Our experience is that exchanges like this work much better in person,
-where we can bounce ideas around in ways that are hard to replicate in writing.
+{\bf We will not give you written feedback} on your ideas, but {\bf we would be happy to talk in person}, either before class or another time.
+Our experience is that exchanges like this work much better in person, where we can bounce ideas around in ways that are hard to replicate in writing.
 
@@
 \item {\bf Final project.}
-You should submit your {\bf Jupyter notebook\/} to \href{mailto:nyu.databootcamp@gmail.com}{nyu.databootcamp@gmail.com}
-by the due date listed on the course website.
-The subject line should be:  ``bootcamp project ug'' or ``bootcamp project mba''
-depending on the section you are in.
-The file name should be your last names separated by dashes and a short title ---
-something like {\tt Jones-Smith-Zhang-India.ipynb}.
+You post your {\bf Jupyter notebook\/} to your GitHub account by the due date listed on the course website.
+You should create a repository called {\tt Data-Bootcamp-Final-Project} and then post your Jupyter notebook.
+Exact protocol of naming file will be announced soon.
 
@@
 \end{itemize}
+
+\newpage
 
@@
 \pagebreak
-\thispagestyle{empty}
-\input{../LaTeX/header.tex}
+
+%\thispagestyle{empty}
+%\input{../LaTeX/header.tex}
 

### 2017-09-06 Documents/bootcamp_topic_intro.tex
Added Atom to intro outline

@@
 
+\section*{\href{https://atom.io/}{Atom}}
+\begin{itemize}
+\item A versatile, text editor. Must have tool for serious work.
+\item We will use it to open files, look at them, learn some markdown.
+\item Lets install it
+\begin{itemize}
+\item Put red sticker on your laptop
+\item Google ``atom download'' or borrow a USB drive
+\item Download or copy installer to your computer
+\item Run installer
+\item Start Atom
+\item Replace red sticker with green when Atom opens
+\end{itemize}
+\item Go and open new file
+\item type my first file, then comma, then birth year, then comma, high school graduation year, then comma, college graduation year (or expected graduation year). For me it is like this\\
+    \\
+{\tt my first file, 1978, 1996, 2001} 
+\item Save as {\tt my-first-file.csv} in your \verb|Data_Bootcamp| file.
+\item \textbf{Pro-tip: naming convention and file type is important in this course}
+\end{itemize}
+
 \section*{\href{https://github.com}{GitHub}}
@@
 \end{itemize}
+\item Now lets use it
+\begin{itemize}
+\item Create a new repository and name it {\tt my-first-repository},
+\item place the {\tt my first file.csv} file you created in it,
+\item Great job! Next class, I'm going to try and ``pull'' the file and then report some statistics about the class to you.
+\end{itemize}
 \end{itemize}
@@
 \item Google ``anaconda download'' or borrow a USB drive
-\item Download or copy installer to your computer --- {\bf Python 3.5!}
+\item Download or copy installer to your computer --- {\bf Python 3.6!}
 \item Run installer

### 2017-09-06 Documents/bootcamp_syllabus.tex
Updated Syllabus

@@
 \vspace{-0.15in}
-%
+
+\textbf{Note we will NOT use NYU Classes.}
+
 The {\bf book\/} has its own site,
@@
 There's a link to it on the course site.
-We will not use NYU Classes.
 
@@
 There are three such assignments in the first month.
-We encourage you do to all of them --- they're good practice ---
+We encourage you do to all of them|they're good practice|
 but your grade will be based on the best two. We find that people who finish these assignments
@@
 Python is not something you can learn from reading a book and attending lectures.
-You need to {\bf write programs\/} ---
-the more the better --- to understand how they work.
+You need to {\bf write programs\/}|
+the more the better|to understand how they work.
 Think about how you'd learn to play basketball or soccer;

### 2017-09-06 Documents/bootcamp_3ideas.tex
Intro outline, 3 ideas modified

@@
 \begin{document}
+
+\centerline{\Large \bf Thinking about data}
+\bigskip
+
+\begin{itemize}
+
+\item Data + Picture = a compelling way to tell a story
+
+\item Where we're headed
+\begin{itemize}
+\item Think of a {\bf graph\/} you'd like to produce -- a ``visualization''
+\item And the {\bf story\/} it tells
+\item And the {\bf data\/} that went into it
+\end{itemize}
+
+\item Examples (links on {\it Topic outlines \& links\/} page) [Gapminder]
+
+\item Questions about graphs
+\begin{itemize}
+\item What did you learn, what is the {\bf story\/}?
+\item {\bf What else} would you like to know?
+\item Where did the {\bf data\/} come from?
+\end{itemize}
+
+\item Examples revisited, answer the questions
+
+\item Course projects
+\begin{itemize}
+\item Course structure:  tools, project
+\item Opportunity to show off your skills (Projects directory of GitHub repo)
+\item First step:  develop project ideas ({\bf ideas are developed, not discovered})
+\item What interests {you}? (finance? movies?  soccer?)
+\end{itemize}
+
+\item Idea machines
+\begin{itemize}
+\item Start with an idea or subject (what interests you?)
+\item Start with a dataset (you'll know more shortly)
+\item Start with an example (see link on data page)
+\item Start with a suggestion from the people you work with
+\end{itemize}
+
+\item Three ideas
+\begin{itemize}
+\item Put red sticker on your computer
+\item Goal:  write down three ideas, 1-2 sentences each (see handout)
+\item Use your imagination, don't overthink it (improv: what's your name?)
+\item Talk to your neighbors, bounce ideas around
+\item Or look at the {\it Data sources\/} page of the course website
+\item When you're done, switch to green sticker
+\item Share an idea with the class, ask for suggestions for developing further
+\item Save ideas for future reference
+\item Optional:  leave a copy with me
+\end{itemize}
+\end{itemize}
+
+\newpage
+
 \bigskip
 \centerline{\Large \bf Data Bootcamp: Three Project Ideas}
-\medskip
-\centerline{Revised: \today}
 

### 2017-09-06 Documents/bootcamp_topic_intro.tex
Intro outline, 3 ideas modified

@@
 \begin{itemize}
-\item  First-day handouts:  Syllabus, Project Guide, Due Dates
-\item  Today's handouts:  this outline, three ideas (two copies), book chapters, red/green stickers
+\item  Today's handouts:  Syllabus, due dates, this outline, red/green stickers
 \item  All posted on website (except the stickers).
@@
 {\tt my first file, 1978, 1996, 2001} 
-\item Save as {\tt my-first-file.csv} in your \verb|Data_Bootcamp| file.
+\item Save as: \verb|my-first-file.csv| in your \verb|Data_Bootcamp| file.
 \item \textbf{Pro-tip: naming convention and file type is important in this course}
@@
 \item Create a new repository and name it {\tt my-first-repository},
-\item place the {\tt my first file.csv} file you created in it,
+\item place the \verb|my-first-file.csv| file you created in it,
 \item Great job! Next class, I'm going to try and ``pull'' the file and then report some statistics about the class to you.
@@
 \item Run program (click on large green triangle)
-\item Look for correct output (last line should be {\tt 3.5.x etc})
+\item Look for correct output (last line should be {\tt 3.6.x etc})
 \item Switch to green sticker if it works
@@
 %Typewriter & \\
+Atom & \\
 Spyder   &                \\
@@
 \end{center}
+
+\item Open Atom and a new file. 
+\begin{itemize}
+\item In a similar fashion as above, create a {\tt .csv } file with the following information separated by commas
+\begin{itemize}
+\item Expected major (or concentration)
+\item Scale of 1-5 (5 being a lot, 1 being none) experience with programming
+\item preferred form of social media
+\item career path (e.g. Finance, Consulting, Technology, Fashion, public policy, rock star)
+\end{itemize}
+\item Name as \verb|my-second-file.csv| and post on GitHub in {\tt my-first-repository}
+\end{itemize}
 
@@
 (There are other files in the same directory, but some of them don't work yet.)
+
 \end{enumerate}
-
-\section*{Thinking about data}
-
-\begin{itemize}
-
-\item Data + Picture = a compelling way to tell a story
-
-\item Where we're headed
-\begin{itemize}
-\item Think of a {\bf graph\/} you'd like to produce -- a ``visualization''
-\item And the {\bf story\/} it tells
-\item And the {\bf data\/} that went into it
-\end{itemize}
-
-\item Examples (links on {\it Topic outlines \& links\/} page) [Gapminder]
-
-\item Questions about graphs
-\begin{itemize}
-\item What did you learn, what is the {\bf story\/}?
-\item {\bf What else} would you like to know?
-\item Where did the {\bf data\/} come from?
-\end{itemize}
-
-\item Examples revisited, answer the questions
-
-\item Course projects
-\begin{itemize}
-\item Course structure:  tools, project
-\item Opportunity to show off your skills (Projects directory of GitHub repo)
-\item First step:  develop project ideas ({\bf ideas are developed, not discovered})
-\item What interests {you}? (finance? movies?  soccer?)
-\end{itemize}
-
-\item Idea machines
-\begin{itemize}
-\item Start with an idea or subject (what interests you?)
-\item Start with a dataset (you'll know more shortly)
-\item Start with an example (see link on data page)
-\item Start with a suggestion from the people you work with
-\end{itemize}
-
-\item Three ideas
-\begin{itemize}
-\item Put red sticker on your computer
-\item Goal:  write down three ideas, 1-2 sentences each (see handout)
-\item Use your imagination, don't overthink it (improv: what's your name?)
-\item Talk to your neighbors, bounce ideas around
-\item Or look at the {\it Data sources\/} page of the course website
-\item When you're done, switch to green sticker
-\item Share an idea with the class, ask for suggestions for developing further
-\item Save ideas for future reference
-\item Optional:  leave a copy with me
-\end{itemize}
-\end{itemize}
 
@@
 \begin{itemize}
-\item If you haven't already:  join the discussion group, take the entry poll.
+\item If you haven't already:  join the discussion group.
 \item Explore the website.  Make sure you can find the book, due dates,

### 2017-09-06 Documents/bootcamp_topic_intro.tex
Fixed Typos

@@
 \item Go and open new file
-\item type my first file, then comma, then birth year, then comma, high school graduation year, then comma, college graduation year (or expected graduation year). For me it is like this\\
+\item type ``my first file'', then comma, then birth year, then comma, high school graduation year, then comma, college graduation year (or expected graduation year). For me it looks like this\\
     \\
@@
 \item place the \verb|my-first-file.csv| file you created in it,
-\item Great job! Next class, I'm going to try and ``pull'' the file and then report some statistics about the class to you.
+\item Great job! \\
+Next class, I'm going to try and ``pull'' the file and then report some statistics about the class to you.
 \end{itemize}

### 2017-09-06 Documents/bootcamp_topic_intro.tex
Fixed Typos

@@
 \firstpageheadrule
-\firstpageheader{\includegraphics[width=0.25\textwidth]{../Figures/stern_black1.pdf}}{}{Data Bootcamp: Three Project Ideas}
+\firstpageheader{\includegraphics[width=0.25\textwidth]{../Figures/stern_black1.pdf}}{}{Data Bootcamp: Getting Started}
 \runningheader{}{}{}
@@
 \item Why bootcamp?
+\item Why me?
 \item Why you?
@@
 
-\section*{Setting up your Computer}
+\section*{Setting up your computer}
 \begin{itemize}
@@
 {\tt my first file, 1978, 1996, 2001} 
-\item Save as: \verb|my-first-file.csv| in your \verb|Data_Bootcamp| file.
+\item Save as: \verb|my_first_file.csv| in your \verb|Data_Bootcamp| file.
 \item \textbf{Pro-tip: naming convention and file type is important in this course}
@@
 \begin{itemize}
-\item Create a new repository and name it {\tt my-first-repository},
-\item place the \verb|my-first-file.csv| file you created in it,
+\item Create a new repository and name it \verb|my_first_repository|,
+\item place the \verb|my_first_file.csv| file you created in it,
 \item Great job! \\
@@
 \end{itemize}
-\item Name as \verb|my-second-file.csv| and post on GitHub in {\tt my-first-repository}
+\item Name as \verb|my_second_file.csv| and post on GitHub in \verb|my_first_repository|
 \end{itemize}

### 2017-09-06 Documents/bootcamp_topic_intro.tex
Edits to Frist day materials

@@
 \item Save as: \verb|my_first_file.csv| in your \verb|Data_Bootcamp| file.
-\item \textbf{Pro-tip: naming convention and file type is important in this course}
+\item \textbf{Pro tip: naming convention and file type is important in this course}
 \end{itemize}
@@
 \item Run installer
-\item Start Launcher (use search box)
-\item Replace red sticker with green when Launcher opens
+\item ONLY FOR PC USERS: on Windows Advanced Installation options, click the box ``Add Anaconda to my PATH environment"
+\item Replace red sticker with green when installation is complete
 \end{itemize}

### 2017-09-06 Documents/bootcamp_topic_intro.tex
Final edits

@@
 \begin{itemize}
-\item  Today's handouts:  Syllabus, due dates, this outline, red/green stickers
+\item  Today's handouts:  Syllabus, this outline, red/green stickers
 \item  All posted on website (except the stickers).
@@
 \item Create \verb|Data_Bootcamp| directory/folder on your computer. This is a place for you to save stuff to, work from, etc.
-\item My style: To keep things simple I do the following
+\item So do this\ldots
 \begin{itemize}
+\item Put red sticker on your laptop
 \item Find your main hard drive, on PCs typically the ``C'' drive
 \item In the C drive, create a folder called \verb|Data_Bootcamp|
+\item Replace red sticker with green!
+\end{itemize}
 \item Now if you every have to call this file you know it is \verb|c:\Data_Bootcamp|
-\end{itemize}
 \end{itemize}
@@
 \begin{itemize}
+\item Put red sticker on your laptop
+\item Sign into github (if you do not have an account, create one)
 \item Create a new repository and name it \verb|my_first_repository|,
 \item place the \verb|my_first_file.csv| file you created in it,
-\item Great job! \\
+\item Great job! Replace red sticker with green!\\
 Next class, I'm going to try and ``pull'' the file and then report some statistics about the class to you.
@@
 
-\section*{Anaconda}
+\section*{\href{https://www.anaconda.com/download/}{Anaconda}}
 

### 2017-09-12 Documents/bootcamp_topic_pyfun1.tex
Updated Outline, Code practice

%%%%%%%%%%%%%%%%%%%%%% Stock Preamble %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{../LaTeX/undergrad_preamble.tex}

%%%%%%%%%%%%%%%%%%%%%%Headers and Footers%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pagestyle{headandfoot}
\runningheadrule
\firstpageheadrule
\firstpageheader{\includegraphics[width=0.25\textwidth]{../Figures/stern_black1.pdf}}{}{Data Bootcamp: Python Fundementals 1}
\runningheader{}{}{}
\runningfooter{}{}{}

\begin{document}
\parskip=\bigskipamount

\bigskip\bigskip
\centerline{\Large \bf Topic Outline:  Python Fundamentals 1}
\centerline{Revised: \today}

\section*{Materials}

\begin{itemize}
\item  Today's handouts:  this outline, code practice, red/green stickers
\item  All posted on {\it Topic outlines \& links\/} page of website (except the stickers).
\end{itemize}

\section*{Our approach}

\begin{itemize}
\item Don't panic.
\item Ask for help if you need it.
\item Newbies:  skip things labelled {\it challenging\/} until you're up to it.
\item Apply effort: we call it {\bf bootcamp} for a reason.
\item {\bf Course-work is front-loaded}:  things will slow down in the second half.
\end{itemize}

\section*{Thinking about data}

Not something we'll talk about much in class for a while, but it should be in the back of
your mind over the next 3-4 weeks.  Keep your eyes open for data you want to work with.
Skim the Data sources page of our website.
Ask for help if you find something you can't handle; we're putting together
a collection of programs that read in a variety of datasets, would be happy to add yours
to the list.

\section*{Preliminaries}

\begin{itemize}

\item Tools and buzzwords
\begin{itemize}
\item Google fu, Spyder, syntax, calculations, assignments, strings, lists, built-in functions, methods, tab completion, object inspector
\end{itemize}

\item {\bf Exercise}
\begin{itemize}
\item Put red sticker on your laptop
\item Start Spyder
\item Point out editor and IPython console
\item Open new (empty) file, save as \verb|bootcamp_class_pyfun1.py| in \verb|Data_Bootcamp| directory/folder.  This will serve as your notes for the class.
%\item Raise your hand if you need help
\item Replace red sticker with green when you're set
\end{itemize}

\item Python programs
\begin{itemize}
\item Syntax:  the rules of Python are less flexible than (say) English
\item Not like Excel: they run line by line, like a book
\item Ours will include:  data input, data management, graphics
\item Examples:  Maddison data, OECD healthcare indicators
\end{itemize}
\end{itemize}

\section*{Python fundamentals 1}

We'll follow the book chapter.
\begin{itemize}
\item Calculations %:  \verb| 2*3, 2 * 3, 2/3, 2^3, 2**3 |
\item Assignments
\item The {\tt print()} function
\item Strings
\item Spyder
\item Help
\item Code cells
\item Comments
\item Quotes
\item Lists
\item Tuples
\item Built-in functions:  {\tt len()}, {\tt type()}, conversions
\item Objects and methods, tab completion
\item Python 2 and 3
\item Review
\begin{itemize}
\item Put red sticker on, replace with green when done
\item Exercises marked challenging are optional
\end{itemize}
\end{itemize}

\section*{After class}

\begin{itemize}
\item Required
\begin{itemize}
%\item Review this chapter
\item Code Practice \#1 due next week (should take about an hour) (we count best 2 of 3)
\end{itemize}
\item Recommended (after every class)
\begin{itemize}
\item {\bf Write}:  Write down everything you remember without using your notes.
\item {\bf Review:} Reread the chapter and fill in anything you missed.
\item Ask for help if you get stuck.
\end{itemize}
\end{itemize}

%\input{../LaTeX/footer.tex}

\end{document}

Second half quiz

How do we get Python help in Spyder?
What's the diff between 'Spencer' and "Spencer"?
What does this do?  x = 7, x = x -3.

### 2017-09-25 Documents/bootcamp_topic_pyfun2.tex
Pyfun2 outline updates

@@
-\documentclass[11pt]{article}
+%%%%%%%%%%%%%%%%%%%%%% Stock Preamble %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\input{../LaTeX/preamble.tex}
+\input{../LaTeX/undergrad_preamble.tex}
 
-% document starts here
+%%%%%%%%%%%%%%%%%%%%%%Headers and Footers%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\pagestyle{headandfoot}
+\runningheadrule
+\firstpageheadrule
+\firstpageheader{\includegraphics[width=0.25\textwidth]{../Figures/stern_black1.pdf}}{}{Data Bootcamp: Python Fundementals 1}
+\runningheader{}{}{}
+\runningfooter{}{}{}
+
 \begin{document}
 \parskip=\bigskipamount
-\parindent=0.0in
-\thispagestyle{empty}
-\input{../LaTeX/header.tex}
 
@@
 \centerline{\Large \bf Topic Outline:  Python Fundamentals 2}
+\medskip
 \centerline{Revised: \today}
@@
 \begin{itemize}
-\item  Today's handouts:  this outline, book chapter, code practice, stickers
-\item  All posted on {\it Topic outlines \& links\/} page of website (except the stickers).
+\item  Today's handouts:  this outline, stickers
+\item  All posted on {\it Topic outlines \& book \& links\/} page of website (except the stickers).
 \end{itemize}
@@
 
-\section*{After class}
+\section*{After this module}
 

### 2017-10-04 Documents/bootcamp_topic_pandas-input.tex
Pands 1 outline update

--- 2017-09-25 Documents/bootcamp_topic_pyfun2.tex
@@
 \firstpageheadrule
-\firstpageheader{\includegraphics[width=0.25\textwidth]{../Figures/stern_black1.pdf}}{}{Data Bootcamp: Python Fundementals 1}
+\firstpageheader{\includegraphics[width=0.25\textwidth]{../Figures/stern_black1.pdf}}{}{Data Bootcamp: Pandas 1}
 \runningheader{}{}{}
@@
 \bigskip\bigskip
-\centerline{\Large \bf Topic Outline:  Python Fundamentals 2}
+\centerline{\Large \bf Topic Outline:  Pandas 1:  Data Input}
 \medskip
@@
 \begin{itemize}
-\item  Today's handouts:  this outline, stickers
-\item  All posted on {\it Topic outlines \& book \& links\/} page of website (except the stickers).
+\item  Today's handouts:  this outline
+\item  All posted on {\it Topic outlines \& links\/} page of website (except the stickers).
 \end{itemize}
@@
 \begin{itemize}
-
 \item Tools and buzzwords
 \begin{itemize}
-\item Boolean variables, comparisons, conditionals ({\tt if}, {\tt else}), slicing,
-loops ({\tt for}), function definitions.
+\item Packages, import, dataframe, csv files, series, columns, index, API.
 \end{itemize}
@@
 \begin{itemize}
-\item \verb|'abcd' |
-\item \verb|['Chase', 'Dave', 'Sarah', 'Spencer'] |
-\item \verb|('Chase', 'Dave', 'Sarah', 'Spencer') |
-\item \verb|'98.76'|
-\item \verb|float('98.76')|
-\item \verb|int(float('98.76'))|
-\item \verb|len('98.76')|
-\item \verb|list('abcd')|
+\item \verb|x = 'abcd'|
+\item \verb|x[1]|
+\item \verb|'abcd'[1]|
+\item \verb|['x1', 'x2']|
+\item \verb|d = {'x1': [1, 5, 3], 'x2': [7, 2, 4]}|
+\item \verb|d['x1']|
+\item \verb|1 > 0|
+\item \verb|type(1>0)|
 \item Tab completion
 \item {\tt object.method?}
-\item Object inspector
+\item Function returns
+\item Objects and methods
 \end{itemize}
@@
 \item Start Spyder
-\item Open new file  \verb|bootcamp_class_pyfun2.py|
-in your \verb|Data_Bootcamp| directory
+\item Open blank file \verb|bootcamp_pandas1.py| to use in class
+\item For second half:  save Python code file in your \verb|Data_Bootcamp| directory: \\
+GitHub $\Rightarrow$ Code $\Rightarrow$ Python $\Rightarrow$ \verb|bootcamp_pandas-input.py|
+$\Rightarrow$ click on Raw button
+\item Raise your hand if you're stuck
 \item Replace red sticker with green when you're set
@@
 
-\section*{Python fundamentals 2}
+\section*{Pandas 1: Data input}
 
@@
 \begin{itemize}
-\item Dictionaries
-\item Logical expressions (comparisons)
-\item Conditionals
-\item Slicing strings and lists
-\item Loops over lists and strings ({\tt for}, {\tt else})
-\item Loops over counters ({\tt range()})
-\item Defining functions
-\item Style
+\item Packages
+\item Importing packages
+\item Properties of dataframes
+\item Working with variables
+\item Dataframe methods
+\item Reading files from your computer
+\item Reading internet files
+\item Examples:  Penn World Table, World Economic Outlook, PISA education data, UN population data and
+projections, income by college major
+\item APIs:  FRED, World Bank, Fama-French equity returns
 \item Review
@@
 
-\section*{After this module}
+\section*{After class}
 
@@
 \begin{itemize}
-%\item Review this chapter
-\item Code Practice \#2 (should take about an hour)
+\item Review this chapter
+\item Code Practice \#3 (due October 20th)\\
+Submit hardcopy of code file \\
+Code template:  GitHub $\Rightarrow$ Code $\Rightarrow$ Python
+$\Rightarrow$ \verb|bootcamp_practice_3_template.py|
+
 \end{itemize}
-\item Recommended
+\item Recommended (always)
 \begin{itemize}

### 2017-12-14 Documents/bootcamp_project_turnin.tex
Final Project Details

%%%%%%%%%%%%%%%%%%%%%% Stock Preamble %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{../LaTeX/undergrad_preamble.tex}

%%%%%%%%%%%%%%%%%%%%%%Headers and Footers%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pagestyle{headandfoot}
\runningheadrule
\firstpageheadrule
\firstpageheader{\includegraphics[width=0.25\textwidth]{../Figures/stern_black1.pdf}}{}{Data Bootcamp: Delivering Your Project}
\runningheader{}{Data Bootcamp: Delivering Your Project}{}
\runningfooter{}{}{}

\begin{document}

\bigskip\bigskip
\centerline{\Large \bf Data Bootcamp:  Delivering Your Project}
\centerline{Revised: \today}

\section*{Overview}

One of our goals is for you to produce a piece of work you can use to demonstrate your data and programming skills to potential employers. The end product should be posted on your GitHub account in a repository so that
you can show others what you've done. You will also be able to see what your classmates have done.

Below are the step by step details and format that I ask of you to post your project in. Not following these instructions exactly will result in a 10 percent reduction in your project score.

\textbf{Due Date: Midnight, at the end of the day December 21st}

\textbf{If you are working in a group, each individual must post the group project on their own GitHub site.} So if Jim and Mary are working together, then Jim posts the project on his site, Mary post the project on her site.

\section*{Step by Step Instructions}

\begin{enumerate}

\item Create a repository on your GitHub site. This repository must be named:

 {\tt Data\_Bootcamp\_Final\_Project}

 \bigskip

\item Populate the repository on your GitHub site with the following items:
\begin{itemize}

\item A readme file (GitHub should populate a blank one for you), that has \textbf{very specific language} specified on the next page. I will not grade your project until this step is complete.

\bigskip

\item Your Jupyter Notebook. This should be titled in the following way:

 {\tt Lastname\_Final\_Project.ipynb}

\bigskip

\item A .pdf file of your Jupyter Notebook. This should be titled in the following way:

 {\tt Lastname\_Final\_Project.pdf}

How to create this: Click on File/Print Preview/Print/ and then there you should be able to select ``Save as PDF''

\end{itemize}

\bigskip

\item Email a a link to your repository to the NYU databootcamp email \href{mailto:nyu.databootcamp@gmail.com}{nyu.databootcamp@gmail.com}

\end{enumerate}

All of this must be done prior to midnight, at the end of the day December 21st. Finally, \textbf{do not modify} your work after the 21st until you have recited a grade from me. After you have received a grade, you may treat the project as yours as continue to work on it as you like.

\section*{The Readme File}

The following text must populate your readme file:
\bigskip
\bigskip

This project was completed by \textbf{insert full name here} in partial fulfilment of  ECON-UB.0232, Data Bootcamp, Fall 2017. I certify that the NYU Stern Honor Code applies to this project. In particular, I have:

Clearly acknowledged the work and efforts of others when submitting written work as
our own. The incorporation of the work of others--including but not limited to their ideas,
data, creative expression, and direct quotations (which should be designated with quotation
marks), or paraphrasing thereof-- has been fully and appropriately referenced using notations
both in the text and the bibliography.

And I understand that:

Submitting the same or substantially similar work in multiple courses, either in the
same semester or in a different semester, without the express approval of all instructors is
strictly forbidden.

I acknowledge that a failure to abide by NYU Stern Honor Code will result in a failing grade for the project and course.

Project Description

\textbf{Insert one paragraph description of your project}

\newpage

\section*{Grading}

Projects will be graded on their overall quality.  This includes, but is not restricted to,
these categories:
%
\begin{itemize}
\item Quality of the idea.  Is the question clearly articulated?  Is it interesting?
Does it have general appeal?
\item Quality of the data.  Does the data support the idea?
Is it the best data for this question?
\item Quality of the code. Is the code readable? Could someone else understand what you were doing and why?
\item Degree of difficulty.  Some ideas are harder than others to implement.
As in Olympic diving, you get credit for taking on a challenge.
\item Professional look.  Does your project look professional?  Are the graphs
easy to understand?  Are they clearly labeled?
\end{itemize}

%\input{../LaTeX/footer.tex}

%\begin{itemize} \itemsep=2\bigskipamount
%\item Clarity of the message
%\item ..
%\end{itemize}

%\input{../LaTeX/footer.tex}

\end{document}

### 2017-12-14 Documents/bootcamp_project_turnin.tex
fixed typo
more typos fixed

@@
 
-Below are the step by step details and format that I ask of you to post your project in. Not following these instructions exactly will result in a 10 percent reduction in your project score.
+Below are the step by step details and format that I ask of you to post your project in.
+Not following these instructions exactly will result in a 10 percent reduction in the available points that your project can receive.
 
@@
 All of this must be done prior to midnight, at the end of the day December 21st.
-Finally, \textbf{do not modify} your work after the 21st until you have recited a grade from me.
+Finally, \textbf{do not modify} your work after the 21st until you have received grade from me.
 After you have received a grade, you may treat the project as yours as continue to work on it as you like.

### 2018-01-16 Documents/bootcamp_syllabus.tex
Updated Spring 2018 Syllabus

--- 2017-08-22 Documents/bootcamp_syllabus.tex
@@
 \firstpageheader{\includegraphics[width=0.25\textwidth]{../Figures/stern_black1.pdf}}{}{Data Bootcamp}
-\runningheader{Data Bootcamp}{}{Syllabus: ECON-UB.0011.02}
+\runningheader{Data Bootcamp}{}{Syllabus: ECON-UB.0232}
 \runningfooter{}{}{}
@@
 \vspace{3mm}
-\centerline{\large\bf ECON-UB.0232 $|$ Fall 2017}
+\centerline{\large\bf ECON-UB.0232 $|$ Spring 2018}
 \vspace{3mm}
@@
 Phone: 212-998-0288\\
-Office hours: TBA, Monday and Wednesday.
+Office hours: TBA
 
 \subsubsection*{Where and When}
-Meeting times: Monday and Wednesday 330-445pm\\
+Meeting times: Tuesday and Thursday 11am-12:15pm
 
-Meeting place: KMC 5-140
+Meeting place: KMC 3-70
+
+\subsection*{Important Dates}
+
+\begin{itemize}
+
+\item Mini-Midterm \#1: February 22nd, 2018. Quick info: Python fundamentals 1-2, 30 minutes, in class, open book, open internet if the wireless is up, bring one page of notes.
+
+\item Mini-Midterm \#2: March 22nd, 2018. Quick info: Intro to Pandas and Matplotlib, 30 minutes, in class, open book, open internet if the wireless is up, bring one page of notes.
+
+\item Three Project Ideas: March 29, 2018. Jupyter Notebook with three project ideas, briefly flushed out and potential data sources. Hard copy due at 5pm.
+
+\item Final Project Proposal + Data Report: April 20th, 2018. Jupyter Notebook with final proposal. More details to be provided. Hard copy due at 5pm.
+
+\item Final Project Due Date: End of Day May 14, 2018
+
+\end{itemize}
 
@@
 \\
-Felipe Alves 
-Email: \href{mailto:mailto:falves@stern.nyu.edu}{falves@stern.nyu.edu}\\
+Vineetha Kutty \\
+Email: \href{mailto:vkk242@nyu.edu}{vkk242@nyu.edu}\\
 Office hours: TBA\\
-
-Guess what\ldots you also have classmates that can help!!!
-You can post questions (and maybe answer your classmates questions) on our discussion group (see below).
-Felipe and I will also monitor the discussion group.
 
@@
 There's a link to it on the course site.
-We will not use NYU Classes.
-
-We have set up {\bf announcement and discussion groups\/} (Google groups)
-to make announcements and post questions. We will use this to post all assignments and
-answer keys.
-If you have coding or other questions, we encourage you to post them there.
-If you know the answer to someone else's question, we {\bf strongly } encourage you to post that, too.
-The links are
-\vspace{-0.1in}
-\begin{center}
-\url{https://groups.google.com/d/forum/databootcamp_fall2017_undergrad} 
-\end{center}
-\vspace{-0.1in}
-You can access the same links from the course website.  Follow the instructions to join under whatever email address you plan to use.
 
@@
 
-The course divides naturally into two parts.
-The first part is an introduction to those aspects of the Python programming language
-useful for data analysis.
+The course divides naturally into three parts. 
+\begin{itemize}
+\item The first part is an introduction to basic aspects of the Python programming language. The mini-midterm \#1 covers this material.
+\item The second part covers data analysis aspects of Python.
+The key tools we will learn about are Pandas and Matplotlib.
 We cover this material with as many applications to real data as we can think of.
-It ends with an exam.
-The second part covers advanced topics and ends with a project of your own.
-The goal is for you to have a piece of work you can show potential employers to
-illustrate your quantitative skill set.
-Both parts include a number of graded deliverables.
-The idea is to {\bf do some work all the time rather than lots of work once in a while.}
-We don't believe the latter will work.
+The mini-midterm \#2 covers this material.
+\item The third covers advanced topics (mostly advanced functionality of Pandas and visualization) and ends with a project of your own.
+The ultimate goal is for you to have a piece of work you can show potential employers to illustrate your quantitative skill set.
+\end{itemize}
+All parts include a number of graded deliverables. The idea is to {\bf do some work all the time rather than lots of work once in a while.} We don't believe the latter will work.
 
 Graded work includes:
-%
 \begin{itemize}
@@
 \item {\bf Code Practice.\/}
-There are three such assignments in the first month.
-We encourage you do to all of them --- they're good practice ---
-but your grade will be based on the best two. We find that people who finish these assignments
-tend to keep up with the material better and these are easy points to get in terms of grades.
-We will also distribute Optional Code Practice ``assignments,''
-but they will not be collected or graded.
-They are, however, a good way to develop your coding skills.
+There are four such assignments in the first month and a half.
+We encourage you do to all of them|they're good practice|but your grade will be based on the best three.
+We find that people who finish these assignments tend to keep up with the material better and these are easy points to get in terms of grades.
 
@@
 
-\item {\bf Examination.\/}
-The exam will cover material from the first half of the course.
-It takes 75 minutes and will be held in class.
+\item {\bf Exams.\/}
+There will be two ``mini'' exams.
+These exams are mini in the sense that they are only 30 minutes long.
 It will involve coding.
-{\bf Bring your computer.\/}
+{\bf Bring your computer.\/} It will be open book, open internet if the wireless is up.
 We suggest you also {\bf bring one page of notes\/}.
@@
 with a {\bf professional piece of data collection and analysis\/}
-that you can share with potential employers.
-The structure of the project is laid out in a separate document. We have found that the quality
+that you can share with potential employers. We have found that the quality
 of final project had a surprisingly low correlation to previous programming experience. A little thought and
@@
 {\bf Due dates} are posted on the course website.
-Assignments, whether code practice or components of the project,
-are due at the start of class on the specified dates.
 
@@
 \begin{tabular}{ll}
-Code Practice (best two of three) & 20\% \\
-Exam        & 30\% \\
+Participation / Professionalism & 5\% \\
+Code Practice (best three of four) & 15\% \\
+Exam \#1        & 15\% \\
+Exam \#2        & 15\% \\
 Project     & 50\% \\
@@
 
-Final grades are not subject to any fixed distribution or curve.
-The number of A grades, for example,
-will depend only on your performance in the course.
-If you make a good-faith effort,
-we expect it to be hard to get less than a B.
-We are the sole judges of what constitutes good-faith effort.
+Final grades are not subject to any fixed distribution or curve. The number of A grades, for example, will depend only on your performance in the course.
 
@@
 If you're an expert, don't worry, we'll cover a lot of material either way.
+
+\section*{Professional Behavior}
+In the interest of having a high-quality experience for all, your classmates and I ask that you:
+\begin{itemize}
+\item Attend. They say ``eighty percent of success is just showing up.'' I see it often, those who show up perform systematically better.
+
+\item Arrive to class on time and stay to the end of the class period. Chronically arriving late or leaving class early is unprofessional and disruptive to the entire class.
+
+\item Eating or drinking in class in any way that interferes with class decorum is inappropriate.
+
+\item Be respectful to myself, the teaching fellow, and your classmates.
+
+\item Join your classmates. Avoid the last row. Be Engaged!
+\end{itemize}
 

### 2018-01-16 Documents/bootcamp_syllabus.tex
Syllabus updates

@@
 Really.  Don't be a hero, ask for help.
+
+Sometimes you want to know more. Below are two resources that I find quite useful:
+\begin{itemize}
+\item \href{https://www.amazon.com/Python-Data-Analysis-Wrangling-IPython/dp/1491957662/}{Python for Data Analysis (2nd Edition)}, by Wes Mckinney.
+Definitive guide to Python for data science and scientific computation, by the creator of Pandas.
+\item \href{https://www.amazon.com/Python-Data-Science-Handbook-Essential/dp/1491912057/}{Python Data Science Handbook}, by Jake VanderPlas.
+Very similar focus as above, extensive chapter on Machine Learning.
+Great GitHub repository with lots of nice, worked out notebooks.
+\end{itemize}
 

### 2018-01-17 Documents/bootcamp_topic_intro.tex
Intro Outline Update, move to jupyter

@@
 
-\section*{\href{https://atom.io/}{Atom}}
-\begin{itemize}
-\item A versatile, text editor. Must have tool for serious work.
-\item We will use it to open files, look at them, learn some markdown.
-\item Lets install it
-\begin{itemize}
-\item Put red sticker on your laptop
-\item Google ``atom download'' or borrow a USB drive
-\item Download or copy installer to your computer
-\item Run installer
-\item Start Atom
-\item Replace red sticker with green when Atom opens
-\end{itemize}
-\item Go and open new file
-\item type ``my first file'', then comma, then birth year, then comma, high school graduation year, then comma, college graduation year (or expected graduation year). For me it looks like this\\
-    \\
-{\tt my first file, 1978, 1996, 2001} 
-\item Save as: \verb|my_first_file.csv| in your \verb|Data_Bootcamp| file.
-\item \textbf{Pro tip: naming convention and file type is important in this course}
-\end{itemize}
-
-\section*{\href{https://github.com}{GitHub}}
-\begin{itemize}
-\item What I will use it for\ldots
-\begin{itemize}
-\item Source of ALL course materials
-\item Place for you to grab materials on the fly. Save files by cut and paste, clever save as, or "Raw" (ask about this)
-\end{itemize}
-\item You need to create an account and email me your username
-\item What you will use it for\ldots
-\begin{itemize}
-\item Post your homework and projects; I will ``pull'' them from there.
-\item Long run: Think of this like an artists portfolio. Here you can post your code and projects and show potential employers, family, friends what you have done.
-\end{itemize}
-\item Now lets use it
-\begin{itemize}
-\item Put red sticker on your laptop
-\item Sign into github (if you do not have an account, create one)
-\item Create a new repository and name it \verb|my_first_repository|,
-\item place the \verb|my_first_file.csv| file you created in it,
-\item Great job! Replace red sticker with green!\\
-Next class, I'm going to try and ``pull'' the file and then report some statistics about the class to you.
-\end{itemize}
-\end{itemize}
-
 \section*{\href{https://www.anaconda.com/download/}{Anaconda}}
@@
 \item Environments?  (Analogy:  Word is an environment for creating Word docs.)
-\item Spyder:  classic coding environment with editor and output windows
 \item Jupyter:  environment for creating IPython notebooks, which combine code with text and output
@@
 \needspace{2\baselineskip}
-\item Run test program in Spyder
+\item Run test program in Jupyter Notebook
 \begin{itemize}
 \item Put red sticker on your laptop
-\item From Launcher, launch Spyder (labelled ``spyder-app'')
-\item Look around (editor, IPython console, Object inspector)
-\item Enter test program in editor (on the left)
-\item Save in \verb|Data_Bootcamp| directory as \verb|bootcamp_test.py|
-(File, Save as, look for folder)
-\item Run program (click on large green triangle)
+\item From Terminal/Command prompt type \verb|jupyter notebook|
+\item Look around...
+\item Enter test program in a code cell
+\item Click on \verb|Untitled| and rename the file as \verb|bootcamp_test|
+\item Click on save button
+\item Click on code cell, press \verb|shift + enter|
 \item Look for correct output (last line should be {\tt 3.6.x etc})
@@
 
-\item Spyder startup summary
+\item Jupyter Notebook startup summary
 \begin{itemize}
-\item Open by typing Launcher in search box (spotlight on Macs), then choose spyder-app.
-\item Or just type Spyder in search box
+\item Open Terminal/Command and type \verb|jupyter notebook|
+\end{itemize}
+\end{itemize}
+
+\section*{\href{https://github.com}{GitHub}}
+\begin{itemize}
+\item What I will use it for\ldots
+\begin{itemize}
+\item Source of ALL course materials
+\item Place for you to grab materials on the fly. Save files by cut and paste, clever save as, or "Raw" (ask about this)
+\end{itemize}
+\item You need to create an account and email me your username
+\item What you will use it for\ldots
+\begin{itemize}
+\item Think of this like an artists portfolio. Here you can post your code and projects and show potential employers, family, friends what you have done.
+\end{itemize}
+\item Now lets use it
+\begin{itemize}
+\item Put red sticker on your laptop
+\item Sign into github (if you do not have an account, create one)
+\item Create a new repository and name it \verb|my_first_repository|,
+\item place the \verb|my_first_file.csv| file you created in it,
+\item Great job! Replace red sticker with green!\\
+Next class, I'm going to try and ``pull'' the file and then report some statistics about the class to you.
 \end{itemize}
@@
 \end{center}
-
-\item Open Atom and a new file. 
-\begin{itemize}
-\item In a similar fashion as above, create a {\tt .csv } file with the following information separated by commas
-\begin{itemize}
-\item Expected major (or concentration)
-\item Scale of 1-5 (5 being a lot, 1 being none) experience with programming
-\item preferred form of social media
-\item career path (e.g. Finance, Consulting, Technology, Fashion, public policy, rock star)
-\end{itemize}
-\item Name as \verb|my_second_file.csv| and post on GitHub in \verb|my_first_repository|
-\end{itemize}
 

### 2018-01-18 Documents/bootcamp_topic_intro.tex
First Class Outline Fixed

@@
 \item Book: \\ \url{https://www.gitbook.com/book/nyudatabootcamp/data-bootcamp/details}
-\item Discussion group: \\ \url{https://groups.google.com/d/forum/databootcamp_fall2017_undergrad}
 \item Data page: \\
 \url{https://nyu.data-bootcamp.com/data/}
-\item GitHub repository:  \url{https://github.com/NYUDataBootcamp/Materials}
+\item NYU Data Bootcamp GitHub repository:  \url{https://github.com/NYUDataBootcamp/Materials}
+\item My Class Specific GitHub repository: \url{https://github.com/mwaugh0328/data_bootcamp_spring_2018}
 \end{itemize}
@@
 \item Create a new repository and name it \verb|my_first_repository|,
-\item place the \verb|my_first_file.csv| file you created in it,
+\item place the \verb|bootcamp_test.ipnyb| file you created in it,
 \item Great job! Replace red sticker with green!\\
-Next class, I'm going to try and ``pull'' the file and then report some statistics about the class to you.
 \end{itemize}
@@
 iTunes & \\
-%Typewriter & \\
-Atom & \\
-Spyder   &                \\
+Typewriter & \\
+Jupyter & \\
+ & .py \\
 \bottomrule
@@
 
-\item Run the \verb|Maddison_data_input.py| Python code example.
+\item Run the \verb|maddison_data_input.ipnyb| Python code example.
 \begin{itemize}
-\item Go to the \verb|Data_Bootcamp| GitHub repository (link above).
-\item Navigate to the {\tt Code} directory and {\tt Lab} subdirectory.
-\item Get \verb|Maddison_data_input.py|
+\item Go to my \verb|data_bootcamp_fall_2018| GitHub repository (link above).
+\item Click on week1, get \verb|maddison_data_input.ipnyb|
 \begin{itemize}
-\item Cut and paste into blank file
-\item Or:  Save file in \verb|Data_Bootcamp| directory (ask how)
+\item Right click on raw
+\item Click \verb|save link as| then your folder window with directory should pop open, save it in your data
 \end{itemize}
-\item Open file in Spyder (File, Open).
-\item Run it by clicking on large green triangle.
+\item Open file in Jupyter.
+\item Run it by clicking on \verb|Cells|, then select \verb|All|
 \item What do you see?
 \end{itemize}
-
-\item {\it Only if you have time.\/} Try this program: \verb|OECD_health_indicators.py|.
-What do you see?  What questions does it raise?
-(There are other files in the same directory, but some of them don't work yet.)
 

### 2018-01-29 Documents/bootcamp_syllabus.tex
doument update

@@
 
-This course has a strong {\bf support system\/} to help you when you run into problems|and anyone who codes runs into problems.
-We have a myself and a teaching fellow to help.
-Below is the contact info for our teaching fellow this semester.
+This course has a strong {\bf support system\/} to help you when you run into problems|and anyone who codes runs into problems. The bottom line:  {\bf If you're stuck, ask for help\/}.
+Really.  Don't be a hero, ask for help.
+
+We have a myself and a teaching fellow to help. Below is the contact info for our teaching fellow this semester.
 
@@
 Office hours: TBA\\
-
-The bottom line:  {\bf If you're stuck, ask for help\/}.
-Really.  Don't be a hero, ask for help.
+\\
+\textbf{My email policy.} During day time on weekdays, I generally answer email (\href{mailto:mwaugh@stern.nyu.edu}{mwaugh@stern.nyu.edu}) quickly.
+During evenings and weekends, you should expect that my response will be less prompt.
+My official policy is that I reserve the right to get back to you within 24 hours.
+If I don't, feel free to email me again.\\
 
@@
 
-Ethics, disabilities, and many other things are governed by NYU
-and Stern policies.
-If you have questions about them, please ask.
+\begin{itemize}
+\item \textbf{General Behavior.} The School expects that students will conduct themselves with respect and professionalism toward faculty, students, and others present in class and will follow the rules laid down by the instructor for classroom behavior.
+Students who fail to do so may be asked to leave the classroom.
 
-On graded work:
-You may discuss assignments with anyone (in fact, we encourage it),
-but anything you submit, including your code, should be your own.
+\item \textbf{Collaboration on Graded Assignments.} You may discuss assignments with anyone (in fact, we encourage it), but anything you submit, including your code, should be your own.
 Exams should be entirely your own work.
+Violation of this policy will result in a failing grade for the course.
 
-On disabilities:
-If you have a qualified disability that requires academic accommodation,
-please contact the Moses Center for Students with Disabilities
-(\href{http://www.nyu.edu/life/safety-health-wellness/students-with-disabilities.html}{CSD},
-212-998-4980) and ask them to
-send us a letter verifying your registration and outlining the accommodation they recommend.
-If you need to take an exam at the CSD,
-you must submit a completed Exam Accommodations Form to them
-at least one week prior to the scheduled exam time to be assured accommodation.
+\item \textbf{Academic Integrity.}
+\begin{itemize}
+\item Integrity is critical to the learning process and to all that we do here at NYU Stern.
+As members of our community, all students agree to abide by the NYU Stern Student Code of Conduct, which includes a commitment to:
+\item Exercise integrity in all aspects of one's academic work including, but not limited to, the preparation and completion of exams, papers and all other course requirements by not engaging in any method or means that provides an unfair advantage.
+\item Clearly acknowledge the work and efforts of others when submitting written work as one's own.
+Ideas, data, direct quotations (which should be designated with quotation marks), paraphrasing, creative expression, or any other incorporation of the work of others should be fully referenced.
+\item Refrain from behaving in ways that knowingly support, assist, or in any way attempt to enable another person to engage in any violation of the Code of Conduct.
+Our support also includes reporting any observed violations of this Code of Conduct or other School and University policies that are deemed to adversely affect the NYU Stern community.
+\end{itemize}
+The entire Stern Student \href{http://www.stern.nyu.edu/sites/default/files/assets/documents/con_039512.pdf}{Code of Conduct} applies to all students enrolled in Stern courses.
+Discussion of this code of conduct and its application to the undergraduate college is here: \href{http://www.stern.nyu.edu/uc/codeofconduct}{Undergraduate College Conduct}.
+\textbf{Any violation of the a policies pertaining to Academic Integrity will result in a failing grade for the course.}
+\end{itemize}
+
+\subsubsection*{Students with disabilities}
+
+If you have a qualified disability that requires academic accommodation during this course,
+please contact the Moses Center for Students with Disabilities (CSD, 212-998-4980) and ask them to
+send me a letter verifying your registration and outlining the accommodation they recommend.
+If you need to take an exam at the CSD, you must submit a completed Exam Accommodations Form to them
+at least one week prior to the scheduled exam time to be guaranteed accommodation.
 

### 2018-05-01 Documents/bootcamp_project_turnin.tex
turn in instructions

@@
 
-\textbf{Due Date: Midnight, at the end of the day December 21st}
+\textbf{Due Date: Midnight, May 14, 2018}
 
@@
 
-All of this must be done prior to midnight, at the end of the day December 21st.
-Finally, \textbf{do not modify} your work after the 21st until you have received grade from me.
+All of this must be done prior to midnight, at the end of the day May 14.
+Finally, \textbf{do not modify} your work after the 14th until you have received grade from me.
 After you have received a grade, you may treat the project as yours as continue to work on it as you like.
@@
 
-This project was completed by \textbf{insert full name here} in partial fulfilment of  ECON-UB.0232, Data Bootcamp, Fall 2017.
+This project was completed by \textbf{insert full name here} in partial fulfilment of  ECON-UB.0232, Data Bootcamp, Spring 2018.
 I certify that the NYU Stern Honor Code applies to this project.
